For $P \to U$ a $G$-torsor. We denote by $P^{[d]} \to U^{(d)}$ the corresponding $G$-torsor over $U^{(d)}$.
Let $\eta^i$ be the generic point of the exceptional divisor $E^i$ of the blowup of $C^{(d_i n_i)}$ by $n_i P_i$
(Where $deg P_i = d_i$).
Where $P_i \in C \setminus U$
We want to prove:
\begin{prop}
    If $ram P^{[d_1n_1]}_{\eta^1} \leq k_1 $ and $ram P^{[d_2n_2]}_{\eta^2} \leq k_2 $
    Then $ram P^{[d_1n_1 + d_2n_2]}_{\eta} = max(k_1, k_2)$ where $\eta$ is the generic point of the exceptional divisor $E$ of the blowup of $C^{(d_1 n_1 + d_2n_2)}$ by $\mdls= n_1 P_1 + n_2P_2$
\end{prop}

We will work this out along an example:
Let $X=\bG_m=\spec R[t, t^{-1}]$ and Let $\cP=\bG_m \xrightarrow[]{(\cdot)^{n}} G_m$ be the $n$'th power map.
It is a $G=\Z/n\Z$ torsor.
The ring map is $R[t, t^{-1}] \xrightarrow[]{t \mapsto t^n} R[t, t^{-1}]$
which corresponds to ring extension: $R[t, t^{-1}] \to R[t^{\frac{1}{n}}, t^{-\frac{1}{n}}]$.
The field of fractions of $\bG_m$ is $K(t)$ and the corresponding map between fields of $\cP \to X$
is $K(t) \xrightarrow[]{t \to t^n} K(t)$. which corresponds to the field extension:
$K(t) \hookrightarrow K(t^{\frac{1}{n}}) = K(t)[X]/(X^n -t)$.
Where $K = Frac R$

The points $0, \infty \in \bP^1$ correspond to the local rings
$\Oo_{0} = K[t]_{(t)}$ and $\Oo_{\infty} = K[\frac{1}{t}]_{(\frac{1}{t})}$ of $K(t)$,
which are DVRs. The corresponding valuations of $K(t)$ are given by:
\[
    v_0\left(\frac{f}{g}\right) = \text{maximal exponent } n \text{ s.t. } t^{n} \mid \frac{f}{g}, \quad v_\infty\left(\frac{f}{g}\right) = \deg g - \deg f
\]

So the diagram of the G-torsor $\cP=\bG_m$ over $\bG_m$ is:
\begin{equation}
    \begin{tikzcd}
        & \cP=\mathbb{G}_m \ar[d, "(\cdot)^n"] \\
        \bP^1 & \arrow[l] \bG_m
    \end{tikzcd}
\end{equation}

The bounded ramification condition is given by:
\begin{equation}
    \text{ram } P_{\eta} \leq k
\end{equation}

We wish to understand


In the general case of a $G$ torsor $P \to C$ we have similarly:
$K(C) \cong K(t)$ the function ring of $C$ for some variable $t$ and a finite field extension $K/\F_p(t')$.
If the basefield $K$ contains $n$'th roots of unity, then the torsor is the same... and continue here:
$\Oo_{P_1}$
the same..
and continue.



This follows by the following:
Start talking about local rings, and take everything locally and prove it locally.
\begin{prop}
    Let
\end{prop}sss


\textbf{Proposition 6 is proved in takeuchi's paper \cite{takeuchi2019blow}.}
We show here a simpler proof for a simpler case that we would need.

Let $\cP$ be a $G$-torsor over $U$.
Let $\mdls = n_1 P_1 + n_2 P_2 = \mdls_1 + \mdls_2$ be a modulus on $C$.
Let $X_{\mdls_1}, X_{\mdls_2}$ be the blowups of $C^{(\deg \mdls_1)}, C^{(\deg \mdls_2)}$ by $\mdls_1, \mdls_2$ respectively.  
Let $E_1, E_2$ be the respective exceptional divisors, and let $\eta_1$, $\eta_2$ be their generic points respectively.

\begin{prop}\label{prop:box-tame-ram}
Assume $\cP^{(\deg \mdls_1)}$, $\cP^{(\deg \mdls_2)}$ are tamely ramified on $\eta_1, \eta_2$  respectively.
Then, $\boxP{\cP^{(\deg \mdls_1)}}{\cP^{(\deg \mdls_2)}}$ is tamely ramified on $\eta_1 \times \eta_2 \in C^{(\deg \mdls_1)} \times C^{(\deg \mdls_2)}$
\end{prop}
\begin{proof}
    \textcolor{red}{Write proof here}
\end{proof}

Next, we prove:
\begin{prop}\label{prop:blowup-prop}
    Let $X,Y$ be smooth over $k$. $x\in X, y\in Y$ closed points. Let $\Bl_x(X), \Bl_y(Y), \allowbreak Bl_{(x,y)}(X\times_k Y) $ be the respective blowups. 
    Let $\eta_X, \eta_Y,\eta_{X\times Y}$ be the generic points of the exceptional divisor of the respective blowups. 
    Then, there exists a scheme $\tilde{U}$ and maps $f_1, f_2$ making the diagram commute:
    
    \begin{diagram}
         \begin{tikzcd}
            {} & \tilde{U} \arrow[dl, "f_1"] \arrow[dr, hook, "f_2"] & {} \\
            \Bl_x(X)\times_k \Bl_y(Y) & {} & \Bl_{(x,y)}(X\times_k Y)
        \end{tikzcd}
    \end{diagram}
    such that:
    \begin{enumerate}
        \item $f_2$ is open immersion
        \item $f_1$ is open map (?open immersion?)
        \item $\eta_{X\times Y} \in \tilde{U}$
        \item $\eta_{X\times Y} \overset{f_1}{\mapsto} \eta_X \times \eta_Y$ 
    \end{enumerate}
\end{prop}

Let $P^{[d]} \to U^{(d)}$ be the corresponding $G$-torsor over $U^{(d)}$.


\begin{lemma}\label{lemma:boxplus}
Let $p: C^{(d)} \times_k C^{(n-d)} \xrightarrow[]{+} C^{(n)}$ be the plus map, restricting $p$ to $U^{(d)} \times_k U^{(n-d)}$ we get a map 
$$p: U^{(d)} \times_k U^{(n-d)} \xrightarrow[]{p} U^{(n)}$$
Then, $$p^* (\cP^{(n)}) \cong \boxPp {\cP^{[d]}}{\cP^{(n-d)}}[k]$$
\end{lemma}

\begin{prop}
    Combinining \Cref{prop:box-tame-ram}, \Cref{prop:blowup-prop} and \Cref{lemma:boxplus} we get that if $P^{[d_1 n_1]}$, $P^{[d_2 n_2]}$ are tamely ramified on $\eta_1, \eta_2$ respectively, then $P^{[d_1 n_1 + d_2 n_2]}$ is tamely ramified on $\eta$ the generic point of the exceptional divisor of the blowup of $C^{(d_1 n_1 + d_2 n_2)}$ by $\mdls = n_1 P_1 + n_2 P_2$.
\end{prop}

\textbf{A few notes}
\begin{enumerate}
    \item takeuchi's paper \cite{takeuchi2019blow} proves a more general version of \Cref{prop:blowup-prop} for arbitrary ramificiation, not necessarily smooth over a field.
    more generally, he proves:
        \begin{prop}\label{prop:ram-blowup}
        If $ram P^{[d_1n_1]}_{\eta^1} = k_1 $ and $ram P^{[d_2n_2]}_{\eta^2} = k_2 $
        Then $ram P^{[d_1n_1 + d_2n_2]}_{\eta} = max(k_1, k_2)$ where $\eta$ is the generic point of the exceptional divisor $E$ of the blowup of $C^{(d_1 n_1 + d_2n_2)}$ by $\mdls= n_1 P_1 + n_2P_2$
        \end{prop}

    \item more generally, the above works for any finite number of points $P_i$ with multiplicities $n_i$. the generalizaiton is easy.
    
\end{enumerate}
\textcolor{red}{ass somewhere the defintiion of box product}