\section{Preliminaries}
\textcolor{red}{Where is the first time you introduce $\cP$ instead of $P$, mark it down, and explain}
In this section we recall the necessariy work, including work from \cite{Guignard2018}, \cite{tendler2015geometricclassfieldtheory} and \cite{takeuchi2019blow}.


\subsection{Algebraic Geometry}
In this section we group together some general theorems in algebraic geometry that we will be employing throughtout the text. 
All schemes are assumed to be locally of finite type. 
\begin{theorem}
    Let $f:X \to Y$ be a finite flat map between integral schemes, of finite type over a field $k$. if $Z \subset X$ is a prime divisor with generic point $\eta_Z$, then $f(Z) \subset X$
    is a prime divisor with generic point $\eta_{f(Z)}$ satisfying $f(\eta_Z)= \eta_{f(Z)}$
\end{theorem}
\begin{proof}
    $f$ is finite hence proper hence closed so $f(Z)$ is closed subset of $Y$, it is irreducible as the image of an irreducible.
    Since $Z = \overline{\{ \eta_Z \}}$ we get: 
    $$\{f(\eta_Z)\} \subset f(Z) = f(\overline{\{\eta_Z\}}) \subseteq \overline{f(\{\eta_Z\})} = \overline{\{f(\eta_Z)\}}$$
    And since $f(Z)$ is closed we get $f(Z) = \overline{\{f(\eta_Z)\}}$.

    For flat map of integral schemes we have for every $x \in X$, $y=f(x)$ the dimension formula:
    $$\text{dim}(\mathcal{O}_{X,x}) = \text{dim}(\mathcal{O}_{Y,y}) + \text{dim}(\mathcal{O}_{X_y, x})$$
    And since $\text{dim}(\mathcal{O}_{X_y, x}) = 0$ we get $\text{dim}(\mathcal{O}_{X,x}) = \text{dim}(\mathcal{O}_{Y,y})$
    concluding that $f(Z)$ is a prime divisor as well. 
\end{proof}

A known theorem states that: 
\begin{theorem}\label{theorem:int_geoint_implies_productint}
    Let $X, Y$ be two integral schemes over a field $k$. If $X$ is geometrically integral then $X \times_k Y$ 
    is integral.
    If both $X,Y$ are geometrically integral, then $X \times_k Y$ is geometrically integral. 
\end{theorem}

\begin{theorem}
    Let $C$ be smooth projective curve geometrically connected over a field $k$. Then:
    \begin{enumerate}
        \item $C^{(d)}$ is smooth
        \item For every $d$, $C^{(d)}$ is integral.
        \item For every $d$, $C^{(d)}$ is geometrically integral.
        \item The product of every finite number of $C^{(d)}$ is geometrically integral. 
    \end{enumerate}
    \begin{proof}
        \begin{enumerate}
            \item Let $t_i$ be a local parameter for $C$ at $P_i$. The local ring of the product $C^d$ at the point $(P_1, \dots, P_d)$ is isomorphic $k[[t_1, t_2, \dots, t_d]]$
            and the local ring of the qoutient at the divisor $D=\sum P_i$ is $k[[t_1, \dots, t_d]]^{S_d}$ which is 
            isomorphic to $k[[t_1, \dots, t_d]]^{S_d} \cong k[[s_1, \dots, s_d]]$ where the $s_i$ are the 
            symmetric polynomials, hence this ring is regular local ring. 
            \item $C$ is irreducible hence $C^{d}$ is irreducible hence $C^{(d)}$ is irreducible. Since $C^{(d)}$ 
            is smooth it is reduced.
            \item By \stackstag{0366}, $C$ is geometrically integral, so it follows from the above. 
            \item \Cref{theorem:int_geoint_implies_productint}
        \end{enumerate}
    \end{proof}
\end{theorem}


\subsubsection*{Blowups}

\begin{theorem}[\stackstag{0805}]
Let $X_1 \to X_2$ be a flat morphism of schemes. Let $Z_2 \subset X_2$ be a closed subscheme. Let $Z_1$ be the inverse image of $Z_2$ in $X_1$. Let $X'_ i$ be the blowup of $Z_ i$ in $X_ i$. Then there exists a cartesian diagram

\[ \xymatrix{ X_1' \ar[r] \ar[d] & X_2' \ar[d] \\ X_1 \ar[r] & X_2 } \]
of schemes.   
\end{theorem}

\begin{theorem}
If $X$ is integral then $Bl_Z(X)$ is integral. %This can be checked locally
\end{theorem}




%%%% %%%% %%%% %%%% %%%% %%%% %%%% %%%%
%               TORSORS
%%%% %%%% %%%% %%%% %%%% %%%% %%%% %%%%
\subsection{Torsors}

Torsors represent a fundamental bridge between two perspectives: they are simultaneously geometric objects amenable to structural manipulation and algebraic entities 
that allow for explicit computation. 
Their characterization as realizations of first cohomology classes, their correspondence with invertible modules over ring objects, 
and their deep-seated connection to Galois theory render them a remarkably flexible and potent tool in arithmetic geometry.

In this section, we provide an overview of the theory of torsors within a topos $\mathcal{E}$, 
with a particular focus on sheaves over the small and big étale sites. 
Let $\mathcal{G}$ be a group object in $\mathcal{E}$. 
We denote by $\mathcal{G}\mathcal{E}$ the category of objects in $\mathcal{E}$ endowed with a left $\mathcal{G}$-action. 
For any object $X \in \mathcal{E}$, there is a canonical identification between the slice category 
$(\mathcal{G}\mathcal{E})/X$ and the category of group objects $\mathcal{G}(\mathcal{E}/X)$, where $X$ is viewed as having the 
trivial $\mathcal{G}$-action.

 We follows notes by Alex Youcis \href{https://alex-youcis.github.io/torsors.pdf}{Notes}



\subsubsection*{Definitions and Basic Properties}
\begin{definition}
    A \textbf{$\mathcal{G}$-torsor} in $\mathcal{E}$ is an object $\mathcal{P}$ of $\mathcal{G}\mathcal{E}$ satisfying the following conditions:
    \begin{enumerate}
        \item The structural morphism $\mathcal{P} \to 1$ is an epimorphism in $\mathcal{E}$ (i.e., $\mathcal{P}$ is locally non-empty).
        \item The map $\mathcal{G} \times \mathcal{P} \to \mathcal{P} \times \mathcal{P}$ defined by $(g, p) \mapsto (g \cdot p, p)$ is an isomorphism in $\mathcal{E}$ (i.e., $\mathcal{G}$ acts simply transitively on $\mathcal{P}$).
    \end{enumerate}
\end{definition}

When $\mathcal{E}$ is the topos of sheaves on a site $\sC$, the definition can be reformulated in terms of local sections. A $\mathcal{G}$-sheaf $\mathcal{P}$ is a $\mathcal{G}$-torsor if:
\begin{enumerate}
    \item For every object $X \in \mathcal{C}$, there exists a covering $\{ U_i \to X \}$ such that $\mathcal{P}(U_i) \neq \emptyset$ for all $i$.
    \item For any $X \in \mathcal{C}$ where $\mathcal{P}(X)$ is non-empty, the action of $\mathcal{G}(X)$ on $\mathcal{P}(X)$ is simply transitively.
\end{enumerate}

A fundamental property of torsors is their local triviality: 
a $\mathcal{G}$-sheaf $\mathcal{P}$ is a $\mathcal{G}$-torsor if and only if it is locally isomorphic to the trivial torsor. 
Specifically, for every $X \in \mathcal{C}$, there must exist a cover $\{ U_i \to X \}$ such that the restriction $\mathcal{P}|_{U_i}$ is 
isomorphic, as a $\mathcal{G}|_{U_i}$-sheaf, to $\mathcal{G}|_{U_i}$ acting on itself by left multiplication.

\subsubsection*{The Category of Torsors}

\begin{definition}
    A \textbf{morphism of $\mathcal{G}$-torsors} $f: \mathcal{P}_1 \to \mathcal{P}_2$ is a morphism of sheaves that is equivariant with respect to the $\mathcal{G}$-action.
\end{definition}

It is a standard result that every morphism of $\mathcal{G}$-torsors is an isomorphism. 
Consequently, the category of $\mathcal{G}$-torsors in $\mathcal{E}$ forms a groupoid.

\begin{definition}
    We denote the groupoid of $\mathcal{G}$-torsors in $\mathcal{E}$ by $\mathbf{Tors}(\mathcal{E}, \mathcal{G})$. The set of isomorphism classes of $\mathcal{G}$-torsors is denoted by $\mathrm{Tors}(\mathcal{E}, \mathcal{G})$,.
    % often identified with the non-abelian cohomology set $H^1(\mathcal{E}, \mathcal{G})$.
\end{definition}

\subsubsection*{Functoriality and the Contracted Product}
Torsors exhibit functoriality with respect to the group object. Let $\varphi: \mathcal{G}_1 \to \mathcal{G}_2$ be a morphism of group 
sheaves on $\sC$, and let $\mathcal{P}$ be a $\mathcal{G}_1$-torsor. We define the \textbf{contracted product} $\mathcal{G}_2 \times^{\mathcal{G}_1} \mathcal{P}$ as the quotient sheaf $(\mathcal{G}_2 \times \mathcal{P}) / \mathcal{G}_1$, where $\mathcal{G}_1$ acts on the product by:
\[ g_1 \cdot (g_2, p) = (g_2 \varphi(g_1)^{-1}, g_1 \cdot p) \]

The contracted product inherits a natural left $\mathcal{G}_2$-action given on local sections by $h \cdot [g_2, p] = [h g_2, p]$, which endows it with the structure of a $\mathcal{G}_2$-torsor. This construction yields a functor:
\[ \varphi_*: \mathbf{Tors}(\mathcal{G}_1) \to \mathbf{Tors}(\mathcal{G}_2), \quad \mathcal{P} \mapsto \mathcal{G}_2 \times^{\mathcal{G}_1} \mathcal{P} \]
On the level of isomorphism classes, $\varphi_*$ induces a map of pointed sets $\mathrm{Tors}(\mathcal{G}_1) \to \mathrm{Tors}(\mathcal{G}_2)$, sending the class of the trivial $\mathcal{G}_1$-torsor to the class of the trivial $\mathcal{G}_2$-torsor.

%%% %%% %%% %%% %%% %%% %%% %%%
%       The Abelian Case 
%%% %%% %%% %%% %%% %%% %%% %%%
\subsubsection*{The Abelian Case}

When $\mathcal{G}$ is a sheaf of abelian groups (an \textit{abelian sheaf}), the pointed set $\mathrm{Tors}(\mathcal{G})$ 
inherits the structure of an abelian group. 

Let $\mathcal{P}_1$ and $\mathcal{P}_2$ be objects of $\mathbf{Tors}(\mathcal{G})$. We define their sum $[\mathcal{P}_1] + [\mathcal{P}_2]$ to be the class $[\mathcal{P}_3]$, where $\mathcal{P}_3$ is the quotient sheaf $(\mathcal{P}_1 \times \mathcal{P}_2)/\mathcal{G}$. In this construction, $\mathcal{G}$ acts on the product $\mathcal{P}_1 \times \mathcal{P}_2$ on $T$-points by:
\[ g \cdot (f_1, f_2) := (g f_1, g^{-1} f_2) \]

The group object $\mathcal{G}$ then acts on the resulting quotient via its action on the presheaf quotient, which is given on classes by:
\[ g \cdot [(f_1, f_2)] = [(g f_1, f_2)] = [(f_1, g f_2)] \]
where the square brackets denote the class in the quotient set. This structure turns $\mathrm{Tors}(\mathcal{G})$ into an abelian group, where the identity is the class of the trivial torsor and the inverse is obtained by the opposite action.

Equivantly, the sum is obtained as the contracted product of the $\cG \times \cG$-torsor $\cP_1 \times \cP_2$ along the multiplication map
$m: \cG \times \cG \to \cG$. 


%%% %%% %%% %%% %%% %%% %%% %%%
%       Torsors as Spaces
%%% %%% %%% %%% %%% %%% %%% %%%
\subsubsection*{Torsors as Flat Spaces}
\textcolor{red}{change Fl to be straight}
We now fix a scheme $X$. We start by focusing on the big fppf site. $X_{Fl}$.
Let $\cG$ be a group sheaf on $X_{Fl}$. A flat-torsor $\cG$-torsor on $X$ is just a $\cG$-torsor on the site $X_{Fl}$.

To the end of this section assume \textbf{$G$ is a flat affine-algebraic $X$-group. } (\textcolor{red}{which by descent is associated also to a group sheaf})
\begin{definition}
Define a \textit{principal $G$-bundle} (or \textit{principal homogenous space} for $G$) to be 
a flat finite presentation $X$-scheme $f : Y \to X$ with an action of $G$ satisfying the following equivalent properties:
\begin{enumerate}
    \item The morphism $Y \times_X G \to Y \times_X Y$ defined on $T$-points by sending $(y, g) \in Y(T) \times G(T)$ to $(y, gy)$ is an isomorphism of $X$-schemes.
    \item There exists an open covering $\{U_i \to X\}$ in $X_{\text{fl}}$ such that $Y_{U_i}$ is isomorphic, as a $G_{U_i}$-space, to $G_{U_i}$ with its left multiplication action.
\end{enumerate}
\end{definition}

Similarly to the case of $G$-torsors of a topos, we define a morphism of principal $G$-bundles to be a morphism of $X$-schemes commuting with the
$G$-action. We now have:
\begin{theorem} 
    The morphism sending $Y \mapsto \mathrm{Hom}_X(-, Y)$ is an equivalence of categories from the category of principal $G$-bundles 
    to the category of $G$-torsors on $X_{\mathrm{Fl}}$. 
    Similarly, the morphism sending $Y$ to $\mathrm{Hom}_X(-, Y)$ to the category of $G$-torsors on $X_{\mathrm{fl}}$ is an equivalence.
\end{theorem}

\begin{cor}
    There is a natural equivalence $\mathbf{Tors}(X_{\mathrm{fl}}, G) \cong \mathbf{Tors}(X_{\mathrm{Fl}}, G)$ inducing a bijection of pointed sets $\mathrm{Tors}(X_{\mathrm{fl}}, G) \xrightarrow{\cong} \mathrm{Tors}(X_{\mathrm{Fl}}, G)$ which is an isomorphism of abelian groups if $G$ is abelian.
    And every $G$-torsor, in each of the above sites can be realized as a scheme, which is a prinicipal $G$-bundle.
\end{cor}


%%% %%% %%% %%% %%% %%% %%% %%%
%       Torsors as Etale Spaces
%%% %%% %%% %%% %%% %%% %%% %%%
\subsubsection*{Torsors as Etale Spaces}
Let $X$ be a scheme, and let $G$ be affine algebraic $X$-group. 
For any topology $\mathcal{T}$ on $\text{Sch}/X$ coarser than the flat topology, we say that 
a flat torsor $\mathcal{P}$ for $G$ is \textit{locally trivial for the $\mathcal{T}$ topology} 
if, in fact, one can find a covering $\{U_i \to X\}$ in $\mathcal{T}$ such that $\mathcal{P}(U_i)$ 
or, equivalently, $\mathcal{P}_{U_i}$ is isomorphic to the trivial torsor for all $i$.

Then, it is immediate that $\Tors(X_{Et, G})$ is canonically isomorphic as pointed sets (abelian groups if $G$ is abelian)
to the subset of $\Tors(X_{Fl}, G)$ consisting of that flat torsors locally trivial for the etale topology.

For the small sites we have:
\begin{theorem}
    If $G$ is smooth affine $X$ group, then any $G$-torsor $\cP$ on $X_fl$ is locally trivial for the etale topology.
\end{theorem}

\begin{cor}\label{cor:tors_etale_flat_eq}
    If $G$ is smooth affine $X$ group, then there is a canonical bijection of pointed sets (abelian groups if $G$ is abelian)
    $\Tors(X_{et}, G) \cong \Tors(X_{fl}, G)$
\end{cor}

And we also have:
\begin{theorem}
    If $G$ is a smooth algebraic $X$-groupm there every flat $G$-torsor is locally trivial for the etale topology and every principal 
    $G$-bundle $Y \to X$ is smooth. In other words the inclusion $\bTors(X_{Et}, G) \to \bTors(X_{Fl}, G)$ is actuall an isomorphism. ??(of what? of categories?)
\end{theorem}

\textcolor{red}{see which of the above theorems we leave intact, cuase it doesn't seem like we need all three}

We now focus on the etale-topology which is coarser then the flat topology. 
Two theorems summarize what happends over the big and small sites:


%%% %%% %%% %%% %%% %%% %%% %%%
%       Torsors and Cohomology
%%% %%% %%% %%% %%% %%% %%% %%%

\subsubsection*{Torsors and Cohomology}
We qoute without proof:
\begin{theorem}
There is a natural bijection of pointed sets     
$\text{Tors}(\mathcal{G|_T}) \to \check{H}^1(T, \mathcal{G})$. Moreover, if $\mathcal{G}$ is an abelian group sheaf, it's an isomorphism of abelian groups.
\end{theorem}

The idea is that for every $[\mathcal{P}] \in \text{Tors}(T, \mathcal{G})$ 
We 
\begin{enumerate}
    \item Choose a covering $\{U_i \to T\}$ such that $\mathcal{P}(U_i) \neq \emptyset$ for all $i$
    \item choose sections $\alpha_i \in \mathcal{F}(U_i)$
\end{enumerate}

Then we note that for all $(i,j)$ the elements $\alpha_i |_{U_i \times_X U_j}$ and $\alpha_j |_{U_i \times_X U_j}$ differ by a unique element of $\mathcal{G}(U_{ij})$
there exists a unique $s_{ij} \in \mathcal{G}(U_{ij})$ such that $\alpha_i |_{U_i \times_X U_j} = s_{ij}(\alpha_j |_{U_i \times_X U_j})$. 
One can then easily see that $(s_{ij})$ defines an element of  $\check{H}^1(T, \mathcal{G})$
which is independent of the choice of repreantiative $\cP$, choice of covering $\{U_i \to T\}$ and choice of sections.

%%% %%% %%% %%% %%% %%% %%% %%%
%       Constant Finite Group Torsors
%%% %%% %%% %%% %%% %%% %%% %%%

\subsubsection*{Constant Finite Group Torsors}
Let $G$ be a finite group. We denote by $\underline{G}$ the constant group scheme $\underline{G}$ over $X$. Sometimes denoted by $\underline{G}_X$
and is given by $\coprod_{g \in G} X$ with the action shuffeling the $X$'s according to multiplication.

By following the definitions, one sees that if $X$ be a connected scheme and $f : Y \to X$ is a finite Galois cover with Galois group $G$. 
Then, $f : Y \to X$ is a principal $\underline{G}$-bundle.
(Recall that a \textit{finite Galois cover} is a finite étale surjection $Y \to X$ with $Y$ connected and such that 
$G = \text{Aut}(Y/X)$ acts transitively on the geometric points of $Y$ lying over any geometric point of $X$.)

On the otherhand if $f: Y \to X$ is a principal $\underline{G}$-bundle with $Y$ connected, then $Y$ is a finite Galois cover with
automorphism group $G$.

However, not all $G$-torsors are connected. If $H\subset G$ is a proper subgroup then any connected finite etale cover $f: Y \to X$ with 
Galois group $H$ gives rise to a non-connected $\underline{G}$-torsor by looking at the induced $G$-torsor $\varphi_*(Y)$ under the inclusion $\varphi: \underline{H} \to \underline{G}$.
On the otherhand, if we fix a geometric point $\overline{x} \to X$, then to give an homomorphism
$\rho \in \mathrm{Hom}_{\mathrm{cont}}(\pi_1^{\mathrm{et}}(X, x), G)$ is equivilant to give a connected pointed Galois cover
$(Y, \overline{y}) \to (X, \overline{x})$ with Galois group $H=\rho(\pi_1^{\mathrm{et}}(X, x)) \subset G$. 
Thus, pushing forward to $G$ we get a prinicipal $\underline{G}$-bundle. The choice of a different geometric point $\overline{x'} \to X$
differ the homomorphism by an inner automorphism, thus we have:

\begin{theorem}\label{theorem:equivalence_fundamental_covers}
    Let $X$ be a connected scheme and $\overline{x}$ a geometric point of $X$. Suppose in addition that $G$ is a finite abstract group. 
    Define a map
    \begin{equation}
        \mathrm{Hom}_{\mathrm{cont}}(\pi_1^{\mathrm{et}}(X, \overline{x}), G) / \mathrm{Inn}(G) \to \mathrm{Tors}(X_{\mathrm{Fl}}, G) 
    \end{equation}
by sending a homomorphism $\rho : \pi_1^{\mathrm{et}}(X, \overline{x}) \to G$ 
to the principal $G$-bundle $\varphi_*(Y)$ where $Y$ is the principal $\underline{\rho(\pi_1^{\mathrm{et}}(X, \overline{x}))}$-bundle 
obtained above and $\varphi$ is the inclusion $\rho(\pi_1^{\mathrm{et}}(X, \overline{x})) \hookrightarrow G$. Then, the map 
 is a bijection of pointed sets where the trivial homomorphisms
  (which is the only element of its $\mathrm{Inn}(G)$-orbit) is the distinguished element of the left hand side.
\end{theorem}

If $G$ is Abelian then $\mathrm{Inn}(G)$ is trivial, and we obtain:
\begin{cor}\label{cor:abelian_equivilance_fundamental_torsors}
    Let $G$ be a finite Abelian group, $X$ a connected scheme, and $\overline{x}$ a geometric point of $X$. Then, the map from \Cref{theorem:equivalence_fundamental_covers}
     induces an isomorphism of Abelian groups
    \begin{equation}
        \mathrm{Hom}_{\mathrm{cont.}}(\pi_1^{\text{ét}}(X, \overline{x}), G) \xrightarrow{\cong} \Tors(X_{\mathrm{Fl}}, G)
    \end{equation}
\end{cor}

\textcolor{red}{Let us give a final note that, evidently, $\mathrm{Aut}(G)$ acts on $\mathrm{Hom}_{\mathrm{cont.}}(\pi_1^{\text{ét}}(X, x), G)$ on the right, and if we consider the quotient $\mathrm{Hom}_{\mathrm{cont.}}(\pi_1^{\text{ét}}(X, x), G)/\mathrm{Aut}(G)$ we get the pointed set of all connected finite Galois covers of $X$ with Galois group isomorphism to a subgroup of $G$.}



%%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%%
%       Equivalence between Torsors and Invertible Modules
%%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%%

\subsubsection*{Equivalence between Torsors and Invertible Modules}
\textcolor{red}{Edit this completly.}
Let $\mathcal{E}$ be a topos and let $\Lambda$ be a commutative ring object in $\mathcal{E}$. Let $G = \Lambda^\times$ denote the internal group object of units of $\Lambda$.
The following proposition establishes the fundamental dictionary between the geometric theory
of principal homogeneous spaces and the algebraic theory of invertible modules.
This equivalence allows us to transport the monoidal structure from the category of modules
(with the tensor product over $\Lambda$) to the category of torsors (with the contracted product over $G$),
strictly within the categorical framework.

\begin{prop}\label{prop:torsor_module_equivalence}
    There is a canonical equivalence of monoidal categories between the category of $G$-torsors in $\mathcal{E}$ and the category of locally free $\Lambda$-modules of rank 1 in $\mathcal{E}$:
    \[
        \Phi: \mathbf{Tors}(\mathcal{E}, \Lambda^\times) \xrightarrow{\sim} \mathbf{Pic}(\mathcal{E}, \Lambda)
    \]
    The equivalence is defined by the associated module functor:
    \[
        \cP \longmapsto \cP \times^{\Lambda^\times} \Lambda := \Lambda^\times \backslash (\Lambda \times \cP)
    \]
    where the quotient is taken with respect to the diagonal action of $\Lambda^\times$ on $\Lambda \times \cP$. 
    The inverse functor associates to an invertible module $\cF$ its sheaf of basis frames $\underline{\mathrm{Isom}}_\Lambda(\Lambda, \cF)$.
\end{prop}

In light of this canonical equivalence, we will pass freely between the language of $G$-torsors and that of locally free $\Lambda$-modules throughout the text.

For a topos $\cE$, a group object $G$ in $\cE$ and an object $X$ in $\cE$, there is a canonical identification
between $({G\cE})_{/X}$ and $G(\cE_{/X})$, given by endowing $X$ with the trivial $G$-action.

We denote by $\mathbf{Tors}(X, G)$ the category of $G$-torsors over $X$ in $G \cE_{/X}$.
Similarly, for a ring object $\Lambda$ in $\cE$, we denote by $\mathbf{Pic}(X, \Lambda)$ the category of locally free $\Lambda$-modules of rank 1 over $X$ in $\cE_{/X}$.
The above equivilance of categories becomes 
\[
    \Phi_X: \mathbf{Tors}(X, \Lambda^\times) \xrightarrow{\sim} \mathbf{Pic}(X, \Lambda)
\].

For a morphism $f: Y \to X$ in $\mathcal{E}$, the equivalence is functorial with respect to:
\begin{itemize}
    \item \textbf{Torsor Pullback:} $f^{-1}P = P \times_{X} Y$ (Fiber product).
    \item \textbf{Module Pullback:} $f^*\mathcal{L} = \Lambda_Y \otimes_{f^{-1}\Lambda_X} f^{-1}\mathcal{L}$ (Extension of scalars).
\end{itemize}

The following diagram commutes up to natural isomorphism:

\[
\begin{tikzcd}[column sep=large, row sep=large]
\mathbf{Tors}(X, G) \arrow[r, "\Phi_X", "\sim"'] \arrow[d, "f^{-1}"'] & \mathbf{Pic}(X, \Lambda) \arrow[d, "f^*"] \\
\mathbf{Tors}(Y, G) \arrow[r, "\Phi_Y", "\sim"'] & \mathbf{Pic}(Y, \Lambda)
\end{tikzcd}
\]


\subsubsection*{\texorpdfstring{More about $G$-torsors}{More about G-torsors}}
We want to be more explicit about $G$-torsors, so let us recall the definition.

\subsection*{Other Theorems}
\textcolor{red}{Say something about the toposes of Etale and etale, maybe add them up in the notation.}
We recall some propositions about $G$-torsors that will be useful later.

\begin{prop}[\cite{Guignard2018}, Proposition 2.12]\label{prop:torsor_representable}
Let $G$ be a finite abelian group, let $S$ be a scheme, and let $\cP$ be a $G$-torsor over an $S$-scheme $X$ in $S_{\text{Et}}$.
Then the etale sheaf $\cP$ is representable by a finite etale $X$-scheme.
\end{prop}
\begin{cor}[\cite{Guignard2018}, Corollary 2.13]
    Let $G$ be a finite abelian group, let $S$ be a scheme, and let $X$ be an $S$-scheme.
    Then the category of $G$-torsors over $X$ in $S_{\text{Et}}$ is equivalent to the category of $G$-torsors over $X$ (the terminal object) in $X_{\text{ét}}$.
\end{cor}

Next, we recall the definition of the contracted product of torsors, which endows the category of $G$-torsors with a monoidal structure.


\subsection{Symmetric Powers of Schemes and Torsors}
This section reviews the construction of quotients for schemes and torsors under finite group actions, specifically focusing on symmetric powers. 
To ensure these quotients exist as schemes, we utilize the framework of admissible actions from \cite{sga1}. 
Our treatment here closely follows the exposition in \cite{Guignard2018}
The definitions and results presented below are adapted from their work. 
This foundation provides the necessary criteria for admissibility and base change required to define the symmetric powers of a scheme $X$
 and a $G$-torsor $\mathcal{P}$ over $X$.


Let $S$ be a scheme.

\begin{definition}[(\cite{sga1}, V.1.7).]
    \noindent
    \begin{itemize}
        \item Let $T$ be an object of a category $\mathcal{C}$ endowed with a right action of a group $\Gamma$. We say that \textbf{the quotient $T/\Gamma$ exists} in $\mathcal{C}$ if the covariant functor
    \[
    \begin{aligned}
    \mathcal{C} &\to \text{Sets} \\
    U &\mapsto \text{Hom}_{\mathcal{C}}(T, U)^{\Gamma}
    \end{aligned}
    \]
    is representable by an object of $\mathcal{C}$.
    \item Let $T$ be an $S$-scheme. An action of a finite group $\Gamma$ on $T$ is \textbf{admissible} if there exists an affine $\Gamma$-invariant morphism $f : T \to T'$ such that the canonical morphism $\mathcal{O}_{T'} \to f_* \mathcal{O}_T$ induces an isomorphism from $\mathcal{O}_{T'}$ to $(f_* \mathcal{O}_T)^{\Gamma}$.
\end{itemize}
\end{definition}

\begin{prop}
    The following holds:
    \begin{enumerate}
        \item \textbf{(\cite{sga1} V.1.3)}. Let $T$ be an $S$-scheme endowed with an admissible right action of a finite group $\Gamma$. If $f : T \to T'$ is an affine $\Gamma$-invariant morphism such that the canonical morphism $\mathcal{O}_{T'} \to f_* \mathcal{O}_T$ induces an isomorphism from $\mathcal{O}_{T'}$ to $(f_* \mathcal{O}_T)^{\Gamma}$, then the quotient $T/\Gamma$ exists and is isomorphic to $T'$.
        \item \textbf{(\cite{sga1}, V.1.8)}. Let $T$ be an $S$-scheme endowed with a right action of a finite group $\Gamma$. Then, the action of $\Gamma$ on $T$ is admissible if and only if $T$ is covered by $\Gamma$-invariant affine open subsets.
        \item \textbf{(\cite{sga1}, V.1.9)}. Let $T$ be an $S$-scheme endowed with an admissible right action of a finite group $\Gamma$, and let $S'$ be a flat $S$-scheme. Then, the action of $\Gamma$ on the $S'$-scheme $T \times_S S'$ is admissible, and the canonical morphism
            \[
            (T \times_S S')/\Gamma \to (T/\Gamma) \times_S S'
            \]
            is an isomorphism.
    \end{enumerate}
\end{prop}

\begin{prop}[{[SGA1]}, IX.5.8]
Let $G$ be a finite abelian group, let $\cP$ be a $G$-torsor over an $S$-scheme $X$ in $S_{\text{Ét}}$. 
Assume that $\cP$ and $X$ are endowed with right actions from a finite group $\Gamma$ 
such that the morphism $\cP \to X$ is $\Gamma$-equivariant, and that the following properties hold:
\begin{enumerate}
    \item[(a)] The right $\Gamma$-action on $\cP$ commutes with the left $G$-action.
    \item[(b)] The right $\Gamma$-action on $X$ is admissible, and the quotient morphism $X \to X/\Gamma$ is finite.
    \item[(c)] For any geometric point $\bar{x}$ of $X$, the action of the stabilizer $\Gamma_{\bar{x}}$ of $\bar{x}$ in $\Gamma$ on the fiber $\cP_{\bar{x}}$ of $\cP$ at $\bar{x}$ is trivial.
\end{enumerate}
Then the action of $\Gamma$ on $\cP$ is admissible, and $\cP/\Gamma$ is a $G$-torsor over $X/\Gamma$ in $S_{\text{Ét}}$.
\end{prop}


\subsubsection*{Symmetric Powers of Schemes}
Let $X$ be an $S$-scheme and let $d \geq 0$ be an integer. The group ${S}_d$ of permutations of $\llbracket 1, d \rrbracket$ acts on the right on the $S$-scheme $X^{\times_S d} = X \times_S \dots \times_S X$ by the formula
\[
(x_i)_{i \in \llbracket 1, d \rrbracket} \cdot \sigma = (x_{\sigma(i)})_{i \in \llbracket 1, d \rrbracket}.
\]

\begin{prop}[\cite{Guignard2018} Proposition 2.27]
    If $X$ is a scheme, Zariski locally quasi-projective over $S$, then the right action of the symmetric group $S_d$ on the $d$-fold fiber product 
    $X^{\times_S d}$ is admissible. 
    Consequently, the quotient $\mathrm{Sym}_S^d(X) = X^{\times_S d}/S_d$ exists as a scheme over $S$.
\end{prop}
\begin{rem*}
    When the base $S$ is understood from context, this quotient is also denoted by $X^{(d)}$.
\end{rem*}

Guingard shows that when $X=\Spec(B)$ and $S=\Spec(A)$ then $\Sym_{S}^d(X)$ is representable by an affine $S$-scheme (See \cite{Guignard2018} Remark 2.28).

\begin{prop}[\cite{Guignard2018} Proposition 2.28]\label{prop:symmetric_power_flat_base_change}
If $X$ is flat and Zariski-locally quasi-projective over $S$, then $\text{Sym}_S^d(X)$ is flat over $S$. Moreover, for any $S$-scheme $S'$, the canonical morphism
\[
\text{Sym}_{S'}^d(X \times_S S') \to \text{Sym}_S^d(X) \times_S S'
\]
is an isomorphism.
\end{prop}

\subsubsection*{Symmetric Powers of Torsors}
\textcolor{red}{change torsor tensor product to contracted product,
and the analogy with sheaves to tensor product (which it is) below the exposition to be more accurate... }


\textcolor{red}{change below the exposition to be more accurate... }
Let $S$ be a scheme, let $X$ be an $S$-scheme and let $d \geq 1$ be an integer. 
Let $G$ be a finite abelian group, and let $\cP \to X$ be a $G$-torsor over $X$ in $S_{\text{Ét}}$. 
It is easy to show that the sheaf $\cP$ is representable by a finite étale $X$-scheme. (For example \cite{Guignard2018} Proposition 2.12)

For each $i \in \llbracket 1, d \rrbracket$ let $p_i : X^{\times_S d} \to X$ be the projection on $i$-th factor, and let us consider the $G$-torsor
\[
p_1^{-1}\cP \otimes \cdots \otimes p_d^{-1}\cP = G_d \backslash \cP^{\times_S d}
\]
over $X^{\times_S d}$, where $G_d \subseteq G^d$ is the kernel of the multiplication morphism $G^d \to G$. 
The object $G_d \backslash \cP^{\times_S d}$ of $S_{\text{Ét}}$ is too representable by an $S$-scheme which is finite étale over $X^{\times_S d}$. 
The group ${S}_d$ acts on the right on $G_d \backslash \cP^{\times_S d}$ by the formula
\[
(p_i)_{i \in \llbracket 1, d \rrbracket} \cdot \sigma = (p_{\sigma(i)})_{i \in \llbracket 1, d \rrbracket}.
\]
This action of ${S}_d$ commutes with the left action of $G$ on $G_d \backslash \cP^{\times_S d}$.

\medskip

\begin{prop}[\cite{Guignard2018} Proposition 2.32.]\label{prop:symmetric_power_torsor}
If $X$ is Zariski-locally quasi-projective on $S$, then the right action of ${S}_d$ on $G_d \backslash \cP^{\times_S d}$ is admissible, 
so that the quotient $\cP^{(d)}$ of $G_d \backslash \cP^{\times_S d}$ by ${S}_d$ exists as a scheme over $S$. 
Moreover, the canonical morphism $\cP^{(d)} \to \mathrm{Sym}_S^d(X)$ is a $G$-torsor, 
and the morphism
\[
p_1^{-1}\cP \otimes \cdots \otimes p_d^{-1}\cP \to r^{-1}\cP^{(d)}
\]
where $r : X^{\times_S d} \to \mathrm{Sym}_S^d(X)$ is the canonical projection, is an isomorphism of $G$-torsors over $X^{\times_S d}$.
\end{prop}
\textcolor{red}{consider replacing $\cP$ with $P$ because it is a scheme}
\textcolor{red}{Add proposition about how it is being a scheme}



\subsection{Etale Fundamental Groups and Tame Fundamental Groups}
We recall the definition and basic properties of the etale fundamental group, following stacks project 
\stackstag{0BQ6}
\begin{prop}[\stackstag{0C0J}]
Let $f : X \to S$ be a flat proper morphism of finite presentation whose geometric fibres are connected and reduced. Assume $S$ is connected and let $\overline{s}$ be a geometric point of $S$. Then there is an exact sequence

\[ \pi _1(X_{\overline{s}}) \to \pi _1(X) \to \pi _1(S) \to 1 \]
of fundamental groups.
    
\end{prop}

\begin{cor}\label{cor:etale_fundamental_group_smooth_proper}
    Let $f : X \to S$ be a proper smooth morphism of finite presentation whose geometric fibres are connected. Assume $S$ is connected and let $\overline{s}$ be a geometric point of $S$. Then there is an exact sequence

    \[ \pi _1(X_{\overline{s}}) \to \pi _1(X) \to \pi _1(S) \to 1 \]
    of fundamental groups.
\end{cor}
\textcolor{red}{add about tameness?}

%
% Tame Ramification
%

\subsection{Algebraic Preliminaries on Ramification}
\textcolor{red}{change?}
We recall the basic definitions and properties of the ramification of discrete valuations. 
We start with the general case of discrete valuation rings and their integral closures within finite separable field extensions. 
Then, we move to the specific setting of complete discrete valuation rings within Galois extensions, where we describe the ramification filtration of the Galois group via both lower and upper numbering.
We follow \stackstag{0EXQ}, and \cite{serreLF}.

\subsubsection*{Ramification of Discrete Valuation Rings}
Let $A$ be a discrete valuation ring with fraction field $K$. Let $L/K$ be a finite separable field extension. Let $B \subset L$ be the integral closure of $A$ in $L$. Picture:

\[ \xymatrix{ B \ar[r] & L \\ A \ar[u] \ar[r] & K \ar[u] } \]
By \stackstag{032L} the ring extension $A \subset B$ is finite, hence $B$ is Noetherian. 
By \stackstag{00OK} the dimension of $B$ is $1$, hence $B$ is a Dedekind domain, see \stackstag{034X}. 
Let $\mathfrak m_1, \ldots , \mathfrak m_ n$ be the maximal ideals of $B$ (i.e., the primes lying over $\mathfrak m_ A$). We obtain extensions of discrete valuation rings

\[ A \subset B_{\mathfrak m_ i} \]
and hence ramification indices $e_ i$ and residue degrees $f_ i$. We have

\[ [L : K] = \sum \nolimits _{i = 1, \ldots , n} e_ i f_ i \]
by \stackstag{02MJ} applied to a uniformizer in $A$. We observe that $n = 1$ if $A$ is henselian (by \stackstag{04GH} and the fact that $B$ is a domain), e.g. if $A$ is complete.

\begin{definition}\label{definition:tamely_ramified_dvrs}
Let $A$ be a discrete valuation ring with fraction field $K$. Let $L/K$ be a finite separable extension. With $B$ and $\mathfrak m_ i$, $i = 1, \ldots , n$ 
as above, we say the extension $L/K$ is
\begin{enumerate}
    \item unramified with respect to $A$ if $e_ i = 1$ and the extension $\kappa (\mathfrak m_ i)/\kappa _ A$ is separable for all $i$,
    \item tamely ramified with respect to $A$ if either the characteristic of $\kappa _ A$ is $0$ or the characteristic of $\kappa _ A$ is $p > 0$, the field extensions $\kappa (\mathfrak m_ i)/\kappa _ A$ are separable, and the ramification indices $e_ i$ are prime to $p$, and
    \item totally ramified with respect to $A$ if $n = 1$ and the residue field extension $\kappa (\mathfrak m_1)/\kappa _ A$ is trivial.
\end{enumerate}
If the discrete valuation ring $A$ is clear from context, then we sometimes say $L/K$ is unramified, totally ramified, or tamely ramified for short.
\end{definition}

\subsubsection*{Structure Theorems and Some Lemmas}\label{subsubsection:structure_theorems_ramification}
Let $A$ be a complete discrete valuation ring over with uniformizer $\pi$ and residue field $\kappa$, which we assume to be perfect.
When $A$ and $\kappa$ are of the same characteristic $p > 0$, then $A$ contains a coefficient field $k \cong \kappa$ and a well known structure theorem holds: $A = k[[\pi ]] \cong k[[t]]$.
Let $K$ be the fraction field of $A$, then $K=k((\pi))$.
By \textcolor{red}{Kummer theory}, unramified extensions of $K$ correspond to separable extensions of $k$.
The maximal unramified extension of $K$ is $\overline{k}((\pi))$ where $\overline{k}$ is a separable closure of $k$.
 \textcolor{red}{Maybe add something about the above facts.}


%We will need that broad definition of tame ramification in order to deal with higher dimensional schemes, 
%however note that in the case of global and local fields (taking $A$ to be the local ring at a prime of the ring of integers), 
%this definition of tame ramification coincides with the usual one.

\subsubsection*{Classical Ramification Filtration in the Galois Case}
We now recall the classical ramification filtration in the Galois case.
Assume $A,B$ are complete DVRs. And that $L/K$ is Galois with Galois group $G$. 
In that case there is uniformizer $\pi \in B$ such that $B=A[\pi ]$ 
   
We have the ramification filtration of $G$ by lower numbering $(G_i)_{i \geq -1}$, defined by
\[ G_i = \{ \sigma \in G \mid v_B(\sigma (x) - x) \geq i + 1 \text{ for all } x \in B \} \]
where $v_B$ is the valuation on $L$ associated to $B$. 
In particular, $G_{-1} = G$ and $G_0$ is the inertia group of the extension $L/K$. 
We have that $L/K$ is unramified if and only if $G_0$ is trivial, and $L/K$ is tamely ramified if and only if $G_1$ is trivial.
It is easy exercise that in the definition of $G_i$ it is enough to check the condition for the uniformizer $\pi$ of $B$, if we define
$i^L_K(\sigma ) = v_B(\sigma (\pi ) - \pi )$ for $\sigma \in G$, then we have $G_i = \{ \sigma \in G \mid i^L_K(\sigma ) \geq i + 1 \}$.
The groups $G_i$ are normal in $G$ and are trivial for large enough $i$. In a tower of fields $K \subset E \subset L$, where $H=\Gal(L/E)$ we have
\[ G_i \cap H = H_i \] for all $i \geq -1$, which corresponds to the fact that $i^L_E = i^L_K|_{\mathrm{Gal}(L/E)}$.
Ramification groups also behave well with respect to quotients: $G_i H/H=(G/H)_j$.
where \[ j=\frac{1}{e_{L/E}}\sum_{\tau \in H} \min(i^L_K(\tau), i+1)-1 \]
i.e. the quotient of a ramification group is itself a ramification group, but with a different index.
In the literature, one reindexes the ramification groups by defining the Herbrand function $\phi_{L/K} : [-1, \infty ) \to [-1, \infty )$:
\[ \phi_{L/K}(i) = \frac{1}{e_{L/K}}\sum_{\sigma \in G} \min(i^L_K(\sigma), i+1)-1 = \int _0^i \frac{1}{[G_0 : G_t]} dt \]
It is continuous, increasing, piecewise linear function, hence a bijection.
It satisfies $\phi_{L/K}=\phi_{E/K} \circ \phi_{L/E}$ for $K \subset E \subset L$, and $G_iH/H=(G/H)_{\phi_{L/E}(i)}$.
Thus, defining the ramification groups by upper numbering as $G^i = G_{\phi_{L/K}^{-1}(i)}$, we have:
\[ G^i H/H = (G/H)^i \]
for all $i \geq -1$.





\subsection{\texorpdfstring{Tame Ramification and Ramification of $G$-Torsors}{Tame Ramification and Ramification of G-Torsors}}
\textcolor{red}{Unramified scheme morphisms is not the same as unramified extensions of DVRs here, so be careful, and say something about that...}
Regarding Tame Ramification we follow \stackstag{0BSE}. It is worth mentioning \cite{Kerz-Schmidt} for the different notions of tameness in higher dimensions, and to what
extent they agree. 

\subsubsection*{Tame Ramification of etale covering in Codimension 1}
\begin{definition}\label{definition:tamely_ramified_in_codim_1}
Assume we are given:
\begin{enumerate}
    \item a locally Noetherian scheme $X$,
    \item a dense open $U \subset X$
    \item a finite étale morphism $f : Y \to U$
\end{enumerate}
such that for every prime divisor $Z \subset X$ with $Z \cap U = \emptyset $ 
the local ring $\mathcal{O}_{X, \xi }$ of $X$ at the generic point $\xi $ of $Z$ is a discrete valuation ring. 
Setting $K_\xi $ equal to the fraction field of $\mathcal{O}_{X, \xi }$ we obtain a cartesian square
\[ \xymatrix{ \mathop{\mathrm{Spec}}(K_\xi ) \ar[r] \ar[d] & U \ar[d] \\ \mathop{\mathrm{Spec}}(\mathcal{O}_{X, \xi }) \ar[r] & X } \]
of schemes. 
In particular, we see that $Y \times _ U \mathop{\mathrm{Spec}}(K_\xi )$ is the spectrum of a finite separable algebra $L_\xi /K_\xi $. 
Then we say $Y$ is unramified over $X$ in codimension $1$, resp. $Y$ is tamely ramified over $X$ in codimension $1$ if $L_\xi /K_\xi $ is unramified, resp. tamely ramified 
with respect to $\mathcal{O}_{X, \xi }$ for every $(Z, \xi )$ as above, (\Cref{definition:tamely_ramified_dvrs}). 
More precisely, we decompose $L_\xi $ into a product of finite separable field extensions of $K_\xi $ and we require each of these to be unramified, resp. tamely ramified with 
respect to $\mathcal{O}_{X, \xi }$.
\end{definition}

\subsubsection*{Ramification of \texorpdfstring{$G$-Torsors}{G-Torsors} over Curves}
Let $G$ be a finite abelian group.
Let $k$ be a perfect field and let $C$ be a projective smooth
geometrically connected curve over $k$, with genus $g$. Let $\mathfrak{m} = \sum_{i} n_i P_i$ be a modulus (i.e. an effective Cartier divisor) on $C$ 
and let $U = C \setminus \mathfrak{m}$.
Let $\cP$ be a $G$-torsor in $U_{\text{ét}}$.
By \Cref{prop:torsor_representable}, $\cP$ is representable by a finite etale $U$-scheme. 
%The conditions of \Cref{definition:tamely_ramified_in_codim_1} are satisfied. And thus we can speak about $\cP$ being tamely ramified (or unramified) over $C$.

Let $P \in \mdls \subset C$ a closed point. Then $\Oo_{C,P}$ is a discrete valuation ring with fraction field $K_P$.
After completion at the maximal ideal $\mathfrak{m}_P$ we obtain a complete discrete valuation ring $\widehat{\Oo_{C,P}}$ with fraction field $\widehat{K}_P$. 
Restricting the $G$-torsor $\cP$ to $\Spec(K_P),\Spec(\widehat{K}_P)$ we obtain $G$-torsors in $\Spec(\widehat{K}_P)_{\text{Ét}}$, $\Spec({K}_P)_{\text{Ét}}$ as in the diagram below:

\[
\begin{tikzcd}
\cP|_{\Spec(\widehat{K}_P)} \arrow[d, color=purple] & \cP|_{\Spec(K_P)} \arrow[d, color=purple] & \cP \arrow[d, color=purple] \\
\Spec(\widehat{K}_P) \arrow[r] \arrow[d] & \Spec(K_P) \arrow[r] \arrow[d] & U \arrow[d] \\
\Spec(\widehat{\Oo_{C,P}}) \arrow[r] & \Spec(\Oo_{C,P}) \arrow[r] & C
\end{tikzcd}
\]


The $G$-torsor $\cP|_{\Spec({K}_P)} \to \Spec({K}_P)$ is an 
etale covering of $\Spec({K}_P)$.
Hence decompose into a disjoint union of spectra of finite separable field extensions of ${K}_P$.
\[ \cP|_{\Spec({K}_P)} = \bigsqcup_{i} \Spec(M_{i}) \]
where each $M_{i}/{K}_P$ is a finite separable field extension.
Pulling back  by $\Spec(\widehat{K_P})$ we get 
\[ \cP|_{\Spec(\widehat{K}_P)} = \bigsqcup_{i} \Spec(M_{i} \otimes_{{K}_P} \widehat{K_P}) \] 
Each product $M_{i} \otimes_{{K}_P} \widehat{K_P}$ decomposes into a finite product of finite separable field extensions of $\widehat{K_P}$.
\[ M_{i} \otimes_{{K}_P} \widehat{K_P} = \prod_{Q} \widehat{M_{i}}_{,Q} \]
Where $Q$ ranges over primes of $M_i$ above $P$, and each $\widehat{M_{i}}_{,Q}/\widehat{K_P}$ is a completion of $M_i$ at that prime. 

To summarize, we have decomposition:
\[ \cP|_{\Spec(\widehat{K}_P)} = \bigsqcup_{i} \Spec(F_{i}) \]
Where each $F_{i}/\widehat{K_P}$ is a finite separable field extension.

The fact that $\cP$ is a $G$-torsor implies that:
\begin{enumerate}
    \item The fields $F_{i}$ are pairwise isomorphic
    \item The fields $F_{i}$ are Galois over $\widehat{K_P}$ with Galois group isomorphic to a subgroup of $H \subset G$.
    \item The number of components $F_{i}$ is equal to the index $[G:H]$.
\end{enumerate}

We say the ramification of $F_i$ over $\widehat{K_P}$ is bounded by $r$ 
if the ramification group $H^{r}$ (in upper numbering) is trivial.

We say that the $G$-torsor $\cP|_{\Spec(\widehat{K}_P)}$ has ramification at $P$ bounded by $r$ if any of the $F_{i}/\widehat{K_P}$ has ramification bounded by $r$.

We say that the $G$-torsor $\cP$ has ramification at $P$ bounded by $r$ if $\cP|_{\Spec(\widehat{K}_P)}$ has ramification at $P$ bounded by $r$.

Finally,
\begin{definition}
A $G$-torsor $\cP$ on $U_{\text{ét}}$ has \textbf{ramification bounded by} $\mdls=\sum n_i P_i$ \textbf{over} $\Spec(k)$
if for every $i$, the ramification of $\cP|_{\Spec(\widehat{K}_{P_i})}$ at $P_i$ is bounded by $n_i$.    
\end{definition}

\subsubsection*{Alternative Definition of Ramification of \texorpdfstring{$G$-Torsors}{G-Torsors} over Curves}
Choose a geometric point $\bar{s}=\Spec(\bar{k}) \to \Spec(k)$. corresponding to a separable closure $k^{sep}=\bar{k}$ of $k$.
By \Cref{subsubsection:structure_theorems_ramification}, the higher ramification groups considered for $\cP|_{\Spec(\widehat{K}_P)}$
and $\cP_{\bar{k}}|_{\Spec(\widehat{K_P \otimes \bar{k}})}$ are isomorphic.
Thus, we define:


\begin{definition}
A $G$-torsor $\cP$ on $U_{\text{ét}}$ has \textbf{ramification bounded by} $\mdls$ \textbf{over} $\Spec(k)$ if for every geometric point 
$\bar{x}$ of $\mdls$, with image $\bar{s}$ in $\Spec(k)$, the restriction of $\cP$ to 
\[ \Spec(\widehat{\mathcal{O}_{C_{\bar{k}},\bar{x}}}) \times_{C_{\bar{k}}} U_{\bar{k}} \] 
has ramification bounded by the multiplicity of $\mdls_{\bar{s}}$ at $\bar{x}$.
\end{definition}

\textbf{Explanation:} The two definitions are equivalent.
This is immediate as $\Oo_{C_{\bar{k}},\bar{x}}$ is the strict henselization of $\Oo_{C_{\bar(k)},P}$
So after completion it is $\widehat{\Oo_{C_{\bar{k}},\bar{x}}} \cong \widehat{\Oo_{C,P}} \otimes_{k} \bar{k}$.
And taking the product with $Y_{\bar{k}}$ amounts to taking the fraction fields, i.e. we get
$\Spec(\widehat{K_P \otimes \bar{k}})=\Spec(\widehat{K_P} \otimes_k \bar{k})$.

Note that tame ramification and unramifiedness in terms of definition above coincide with the ones in \Cref{definition:tamely_ramified_in_codim_1}.

%%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%%
%       Ramification of $G$-torsors in terms of Characters
%%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%% %%%

\subsubsection*{Ramification of $G$-torsors in terms of Characters}\label{section:ramification_characters}
Since we are working over $X=\Spec(k)$, the group $G$ is $etale$ over $\Spec(k)$
Hence by \Cref{cor:abelian_equivilance_fundamental_torsors} and \Cref{cor:tors_etale_flat_eq} we get an isomosphism of
groups:
$\mathrm{Hom}_{\mathrm{cont.}}(\pi_1^{\text{ét}}(X, \overline{x}), G) \xrightarrow{\cong} \Tors(X_{\mathrm{et}}, G)$

When $X=\Spec(L)$ for a complete valued field $L$, $\pi_1^{\text{ét}}(X, \overline{x})=G_L := Gal(L^{sep}/L)$
Where $L^{sep}$ is a fixed seprable closure. 
And we conclude that $\cP|_{\Spec(L)}$ correspond to a continious homomorphism $\rho: G_L \to G$
and one can check that it has ramificaiton bounded by $r$ if and only if $\rho(G_L^r) = \{ 1\}$.



\subsubsection*{Basic Properties of Ramification of \texorpdfstring{$G$-Torsors}{G-Torsors}}
In this section we prove some basic properties of the ramification of $G$-torsors.

\begin{lemma}\label{lemma:bounding_ramification_of_contracted_product}
    Let $G$ be a finite abelian group and $X$ be a locally Noetherian scheme over a field $k$. 
    Let $U \subset X$ be a dense open subset and let $Z$ be a prime divisor in the complement $X \setminus U$, and let $\xi$ denote its generic point.

    Assume $\cP_1$ and $\cP_2$ are two $G$-torsors on $U_{\text{ét}}$, Such that $\cP_1$ has ramification bounded by $r_1$ at $(Z, \xi)$, and $\cP_2$ has ramification bounded by $r_2$ at $(Z, \xi)$.
    Then their contracted product $\cP_1 \wedge^G \cP_2$ has ramification bounded by $max(r_1, r_2)$ at $(Z, \xi)$.
\end{lemma}
\begin{proof}
    Let $A=\widehat{\Oo_{X, \xi}}$ and let $K=Frac(A)$.
    Let $\rho_1, \rho_2: G_K \to G$ be the associated continious homomorphisms corresponding to the $G$-torsors 
    $\cP_1|_{\Spec(K)}$, $\cP_2|_{\Spec(K)}$.
    Then the associated character to $(\cP_1 \wedge^G \cP_2)|_{\Spec(K)}$ is $\rho=\rho_1 + \rho_2$.
    And the claim follows by \Cref{section:ramification_characters}
\end{proof}

\begin{lemma}\label{lemma:descend_ramification_along_etale}
Let $f: X \to Y$ be a morphism of locally Noetherian schemes. Let $U_X \subset X$ and $U_Y \subset Y$ be dense open subschemes such that $f^{-1}(U_Y) \subset U_X$. 

Let $Z_X$ and $Z_Y$ be prime divisors of $X$ and $Y$ with generic points $\eta_X$ and $\eta_Y$, respectively, such that $Z_X \cap U_X = \emptyset$ and $Z_Y \cap U_Y = \emptyset$. Suppose $f(\eta_X) = \eta_Y$ and that $f$ is étale at $\eta_X$.

Let $\mathcal{P}$ be a $G$-torsor over $U_Y$, and let $f^{-1} \mathcal{P}$ be its pullback to $f^{-1}(U_Y) \subset U_X$. Then, the ramification of $f^{-1} \mathcal{P}$ is bounded by $r$ at $\eta_X$ if and only if the ramification of $\mathcal{P}$ is bounded by $r$ at $\eta_Y$.
\end{lemma}

\begin{proof}
The boundedness of ramification is determined by the behavior of the torsor over the completion of the local rings at the generic points. 

Let $A = \mathcal{O}_{Y, \eta_Y}$ and $B = \mathcal{O}_{X, \eta_X}$ be the discrete valuation rings at the generic points, with fraction fields $K$ and $L$ respectively. Since $f$ is étale at $\eta_X$, the map $A \to B$ is a flat, unramified local homomorphism. Consequently, the extension of completions $\widehat{L} / \widehat{K}$ is a finite unramified extension of complete discretely valued fields.

The upper numbering filtration on the absolute Galois group is compatible with unramified base change. Specifically, let $G_K = \operatorname{Gal}(K^{sep}/K)$ and $G_L = \operatorname{Gal}(L^{sep}/L)$. For an unramified extension, the Herbrand function is the identity, which implies that for any $r \geq 0$:
\[ G_L^r = G_K^r \cap G_L \]
The ramification of the $G$-torsor $\mathcal{P}$ is bounded by $r$ if and only if the corresponding Galois representation $\rho: G_K \to G$ satisfies $\rho(G_K^r) = \{1\}$. 

By the filtration identity above, $\rho(G_L^r) = \{1\}$ if and only if $\rho(G_K^r) = \{1\}$. Thus, the pullback torsor $f^{-1}\mathcal{P}$ has ramification bounded by $r$ at $\eta_X$ if and only if $\mathcal{P}$ has ramification bounded by $r$ at $\eta_Y$.
\end{proof}

\subsubsection*{The ramification in term of morphisms}
maybe not needed. 

% %This is equivilant to homomorphism defintion.%

% Let $k$ be a perfect field and let $X$ be a scheme over $k$.
% Let $G$ be a finite abelian group. Let $P \in X$ be a closed point and let $\cF$ be a local system on $U_P \subset X$.
% \begin{definition}
    
% \end{definition}

\textcolor{red}{EDIT AND REFINE THIS ENTIRE THING.}

\begin{definition}[Version 1: Pure Openness]
Let $C$ be a curve over a field $k$. Let $P \ in C$ be closed point. $U=C-P$ be the complement. Let $\cF$ be a local system on $U$. let $\eta \in P$ be the generic point of $P$ (it is irreducible of codim=1 in $C$)
Then $\cF$ has ramification bounded by $d$ on $P$ if and only if
$\restr{\cF}{\eta}$ is a field extension of ramification bounded by $d$. 
\end{definition}

We want to explain why $\restr{\cF}{\eta}$ is a finite field extension of $k(C)$. We are in the following situation:

\begin{equation*}
\begin{tikzcd}
i^{*}\cF \arrow[d] & \cF \arrow[d] \\
P \arrow[r, "i"] & C          
\end{tikzcd}
\end{equation*}

So, we are asking, what are local system $\cG$ on $P$.
$P=\spec(k(P))$

Version 2: With etale coverings.


\quad what is a local system on $X$, what is a local system on $P \rightarrow C$, what is a local system on $\spec \Oo_P \rightarrow C$


locally constant sheaves are given by: \stackstag{09Y8}

\textcolor{red}{EDIT AN REFINE THIS ENTIRE THING}
The goal is to  1. define what ramificaiton of local system means in different settings
2. explore basic properties and ways to calculate. 

\begin{definition}
    Let $G$ be a finite abelian group and let $d \geq 0$ be a rational number. A $G$-torsor over $\operatorname{Spec}(L)$ (in $\operatorname{Spec}(k)_{\text {Ét }}$ ), corresponding to a continuous homomorphism $\rho: G_L \rightarrow G$, is said to have ramification bounded by $d$ if $\rho\left(G_L^d\right)=\{1\}$. A $G$-torsor over $\operatorname{Spec}(L)$ with ramification bounded by 0 (resp. 1) is said to be unramified (resp. tamely ramified).
\end{definition}

\textbf{Explain why a $G$ torsor over $\Spec(L)$ in 
$\operatorname{Spec}(k)_{\text {Ét }}$} correspond to a continuous homomorphism $\rho: G_{L} \rightarrow G$

\textbf{Explanation:}
Let $L^{sep}$ be a separable closure of $L$, and let $G_L$ be the Galois group of $L^{sep}$ over $L$ then
\begin{enumerate}
    \item the small étale topos of $\Spec(L)$ is isomorphic to the topos of sets with continuous left $G_L$-action.
    \item  By 2.13, the category of $G$-torsors over $\Spec(L)$ in $\Spec(k)_{Et}$ is isomorphic to the category of $G$-torsors
    in the small étale topos $\Spec(L)_{et}$.
    \item  Correspondingly, for each finite abelian group $G$, the group
    of isomorphism classes of the category $Tors(\Spec(L), G)$ is isomorphic to the group of continuous
    homomorphisms from $G_L$ to $G$.
\end{enumerate}
We want to show 3 explicitly. 

\textbf{What is an isomorphism class of "$G$-sets with continuous left $G_L$ action"}
before, we understand 
\textbf{What is an isomorphism class of "sets with continuous left $G_L$ action" is a continuous $G$ action}


We want to show
How, from a $G$-Torsor $P$ in the $\Spec(L)_{et}$ we get a set with ccontinious homomorphism from $G_L$
\textbf{}




\textbf{Example-Explain!!!}

Remark 3.10. If $P \rightarrow \operatorname{Spec}(L)$ is a $G$-torsor in $\operatorname{Spec}(k)_{\text {Ét }}$, then we have a finite decomposition
$$
P=\coprod_{i \in I} \operatorname{Spec}\left(L_i\right)
$$
where each $L_i$ is a finite separable extension of $L$, and are pairwise isomorphic. The $G$-torsor $P$ has ramification bounded by $d$ if and only if for each $i$ (or, equivalently, for some $i$ ) the extension $L_i / L$ has ramification bounded by $d$, in the sense $G_L^d$ acts trivially on the finite set $\operatorname{Hom}_L\left(L_i, L^{\text {sep }}\right)$.

\begin{definition}\label{definition:ulscodim1} let $X$ be good enough (irreducible, regular at codim=1? smooth?), $U$ open subscheme and $Z$ the complemenet which is irreducible closed subscheme of $codim=1$. let $\eta$ be the generic point of $Z$. and let $\cF$ be a local system on $U$ as in:
\begin{equation}
\begin{tikzcd}
               &             & &  \cF \arrow[d]                   \\
\eta \arrow[r] & Z \arrow[r] & X           & U \arrow[l, hook']
\end{tikzcd}
\end{equation}

\textbf{Example-Explain!!!}

Then we say $\cF$ is unramified on $Z$ if and only if $\restr{\cF}{\eta}$ is unramified.

Note that
\end{definition}

\begin{theorem}
let $X,U,Z,\cF$ be as in \cref{definition:ulscodim1}. If $\cF$ is unramified on $Z$, then $\cF$ is pulledback from a local system on $X$
\end{theorem}

Next we have a general proposition.

\begin{prop}
Let $X$ be a normal Noetherian scheme, and let $Z \subset X$ an irreducible closed subscheme of codimension 1 (a prime divisor)
Let $U=X \setminus Z$ be the open complement, and $\eta$ the generic point of $Z$.
Let $f: Y \to X$ be a finite surjective morphism, where $Y$ is also a normal Noetherian scheme.
Suppose there exists an irreducible component $Z' \subset f^{-1}(Z)$ with generic point $\eta'$ such that
$f$ is unramified at $\eta'$. 

Then:

\end{prop}

\begin{proof}
    For clarity, we draw the diagram: 

\begin{diagram}
\begin{tikzcd}[row sep=large, column sep=large]
Z \times_X Y \arrow[r] \arrow[d] & Y \arrow[d, "f"] & U \times_X Y \arrow[l] \arrow[d] \\
Z \arrow[r, "closed"] & X & U \arrow[l, "open"] \\
\end{tikzcd}
\end{diagram}

We have that $\eta' \rightarrow \eta$ is unramified. hence $\cF$ unramified on $\eta$ if and only if $f^*\cF$ is unramified on $\eta$ (from proposition in the beginning)

\end{proof}


%
% SYMMETRIC POWERS OF LOCAL SYSTEMS ON CURVES
%
\subsection{Symmetric Powers of Local Systems on Curves}\label{section:symmetric_powers_on_curves}
\textcolor{red}{don't need modulus in this section, etc.}
Let $k$ be a perfect field. 
Let $C$ be a projective smooth geometrically connected curve over $k$, with genus $g$.
Let $\mdls$ be a modulus on $C$ and let $U = C \setminus \mdls$.
Let $G$ be a finite Abelian group and let $\cP$ be a $G$-torsor on $U$ with ramification bounded by
$\mdls$. Let $d \geq \deg m$.

We have the following diagram:
\[
\begin{tikzcd}
U^{(d_1)} \times_k U^{(d_2)} \arrow[r, "p_1"] \arrow[d, "p_2"] & U^{(d_1)} \\
U^{(d_2)} &  {}
\end{tikzcd}
\] 

pullbacking $\cP^{(d_i)}$ along the projections we get a $G$-torsor

\[\cP ^{(d_1)} \boxtimes \cP ^{(d_2)} = p_1^{-1} \cP^{(d_1)} \otimes p_2^{-1} \cP^{(d_2)}\]
On $U^{(d_1)} \times_k U^{(d_2)}$

Note that the plus map $C^{(d_1)} \times_k C^{(d_2)} \xrightarrow{+}{} C^{(d_1 + d_2)}$
is induced from
\[
\begin{tikzcd}
C^{d_1} \times_k C^{d_2} \arrow[r, "\cong"] \arrow[d, "r_1 \times r_2"] & C^{d_1 + d_2} \arrow[d, "r"] \\
C^{(d_1)} \times_k C^{(d_2)} \arrow[r, "+"] & C^{(d_1+ d_2)} 
\end{tikzcd}
\]


Hence, by \Cref{prop:symmetric_power_torsor} (and replacing $C$ with $U$ above) we get canonical identification:
\[
 (+^{-1})(\cP^{(d_1+d_2)}) \cong \cP ^{(d_1)} \boxtimes \cP ^{(d_2)}
\]


\subsection{Generalized Picard Scheme}
In this section, we recall the notion of generalized Jacobian varieties and study their fundamental properties. The material presented here is primarily adapted from \cite{Guignard2018} and \cite{takeuchi2019blow}. For further background on the general theory of abelian varieties and Jacobians, the reader may also consult \cite{milneAV}.
Let $S$ be a scheme and let $C$ be a projective smooth $S$-scheme whose geometric fibers are connected and of dimension 1. Let $\mdls$ be a modulus on $C$, defined as an effective Cartier divisor of $C/S$ 
(i.e., a closed subscheme of $C$ which is finite flat of finite presentation over $S$).
We denote the projection $C \times_S T \to T$ by $\text{pr}$ for any $S$-scheme $T$.

\subsubsection*{The Functor of Points}
Let $d$ be an integer. For an $S$-scheme $T$, we consider the set of data $(\cL, \psi)$ where:
\begin{itemize}
    \item $\cL$ is an invertible sheaf of degree $d$ on $C_T$.
    \item $\psi: \Oo_{\mdls_T} \xrightarrow{\sim} \cL|_{\mdls_T}$ is a trivialization of $\cL$ along the modulus.
\end{itemize}
Two such pairs $(\cL, \psi)$ and $(\cL', \psi')$ are said to be isomorphic if there exists an isomorphism of invertible sheaves $f : \cL \to \cL'$ such that the following diagram commutes:
\[
\begin{tikzcd}
& \Oo_{\mdls_T} \arrow[dl, "\psi'"'] \arrow[dr, "\psi"] & \\
\cL'|_{\mdls_T} \arrow[rr, "f|_{\mdls_T}"] & & \cL|_{\mdls_T}
\end{tikzcd}
\]
We define the presheaf $\text{Pic}_{C, \mdls}^{d, \text{pre}}$ on $\text{Sch}/S$ by assigning to $T$ the set of isomorphism classes of such pairs. Let $\PicCm[d]$ denote the \'etale sheafification of this presheaf.

\subsubsection*{Representability and Structure}
The fundamental properties of this functor are as follows:
\begin{enumerate}
    \item $\text{Pic}_{C, \mdls}^{d}$ is represented by an $S$-scheme. (Note: If $\mdls$ is faithfully flat over $S$, the presheaf is already a \'etale sheaf).
    \item $\text{Pic}_{C, \mdls}^{0}$ is a smooth commutative group $S$-scheme with geometrically connected fibers, referred to as the \textit{generalized Jacobian variety} of $C$ with modulus $\mdls$.
    \item For any $d$, $\text{Pic}_{C, \mdls}^{d}$ is a $\text{Pic}_{C, \mdls}^{0}$-torsor.
\end{enumerate}
In the case where $\mdls = 0$, we recover the standard Jacobian variety, denoted simply as $\text{Pic}_C^d$.
\subsubsection*{Relation to the Standard Jacobian}
We now examine the behavior of the generalized Picard scheme under the variation of the modulus. By viewing the structure along the modulus as an additional rigidification, we obtain natural transition maps corresponding to the inclusion of moduli.

Let $\mdls_1$ and $\mdls_2$ be moduli such that $\mdls_1 \subset \mdls_2$. There exists a natural map 
\[
\text{Pic}_{C, \mdls_2}^d \to \text{Pic}_{C, \mdls_1}^d
\]
obtained by restricting the isomorphism $\psi$. Since $\mdls_2$ is a finite $S$-scheme, this map is a surjection as a morphism of \'etale sheaves.
In particular, for any modulus $\mdls$, there is a natural surjective morphism of \'etale sheaves:
\[
\text{Pic}_{C, \mdls}^d \to \text{Pic}_C^d.
\]


\subsubsection*{Local Freeness and Base Change}
%\textcolor{red}{there is ${\mdls}$ here - should fix that}
Let $\mdls$ be a modulus which is everywhere strictly positive. Let $g$ denote the genus of $C$, which is a locally constant function on $S$. We restrict our attention to degrees $d$ satisfying the condition:
\begin{equation} \label{equation:degree-condition}
    d \geq \max\{2g - 1 + \deg \mdls, \deg \mdls\}.
\end{equation}

Assuming $S$ is quasi-compact, such a $d$ always exists.

Fix an integer $d$ satisfying the condition above. Let $T$ be an $S$-scheme and let $\cL$ be an invertible sheaf of degree $d$ on $C_T$. One can show that the pushforwards $\mathrm{pr}_* \cL$ and $\mathrm{pr}_* \cL(-{\mdls})$ are locally free sheaves and their formations commute with any base change. Explicitly, for any morphism of $S$-schemes $f : T' \to T$, the base change morphisms are isomorphisms:
\[
    f^* \mathrm{pr}_* \cL \xrightarrow{\sim} \mathrm{pr}_* f^* \cL
\]
and
\[
    f^* \mathrm{pr}_* (\cL(-{\mdls})) \xrightarrow{\sim} \mathrm{pr}_* f^* (\cL(-{\mdls})).
\]
In particular, following \cite{Guignard2018}, if $\cL$ is invertible $\cO_C$-module with degree $d$ satisfying \ref{equation:degree-condition} on each fiber of $f$ then, $\mathrm{pr}_* \cL$ is a locally free $\mathcal{O}_S$-module of rank $d-g+1$.

For further background and verification of these constructions, we refer the reader to Milne's notes on Abelian Varieties (\cite{milneAV}).

\subsection{The Abel-Jacobi Morphism and its Fibers}\label{section:AbelJacobi}


Let $U = C \setminus \mdls$ be the complement of the modulus in $C$.
The effective cartier divisors of degree $d$ which are prime to $\mdls$ are parameterized by the symmetric power $\Sym_S^d (U) = U^{(d)}$ over $S$ (See \cite{Guignard2018} Proposition 4.12, \cite{milneAV} Theorem 3.13).
For any such divisor $D \in U^{(d)}$, the associated line bundle $\Oo_C(D)$ admits a canonical trivialization along $\mdls$. 
Specifically, the canonical section $1_D$ is regular and non-vanishing on $\mdls$ because $\operatorname{supp}(D) \cap \operatorname{supp}(\mdls) = \emptyset$. 
This section restricts to a nowhere-vanishing section on the subscheme $\mathfrak{m}$, thereby determining a trivialization $\psi_D^{-1}: \Oo_C(D)|_{\mdls} \xrightarrow{\sim} \Oo_{\mdls}$.
This is done functorially in families, yielding a morphism from the symmetric power to the generalized Picard scheme (over $S$):
\begin{equation}
    \Phi_{d}: U^{(d)} \to \Pic^d_{C, \mathfrak{m}}, \quad D \mapsto [(\mathcal{O}_C(D), \psi_D)],
\end{equation}

When $\mdls = 0$, $d \geq max \{2g - 1, 0\}$ and $C$ admits a section over $S$, $C^{(d)}$ is a projective space bundle over $\PicC[d]$, 
It is proper, surjective with geometrically connected fibers.

Guignard (\cite{Guignard2018} Theorem 4.14) proves that for $\mdls > 0$ and $d$ satisfying \Cref{equation:degree-condition}, the Abel-Jacobi morphism $\Phi_d$ is 
surjective smooth of relative dimension $d - \deg \mdls - g + 1$, with geometrically connected fibers. 

When $S=\spec (k)$, the geometric-fibers of $\Phi_d$ are well understood:
\begin{theorem}
    Assuming $S=\spec (k)$ and $d \geq max \{2g - 1 + \deg \mdls, \deg \mdls\}$. Then, the geometric-fibers of the Abel-Jacobi morphism $$ \Phi_d : U^{(d)} \to \PicCm[d] $$ over any point are isomorphic to
$$
\begin{cases}
\mathbb{A}_{k^{sep}}^{d - \deg \mdls - g + 1} & \text{if } m > 0 \\
\mathbb{P}_{k^{sep}}^{d - g} & \text{if } m = 0
\end{cases}
$$
In both cases $\Phi_d$ is a fibration in affine spaces or projective spaces, depending on whether $\mdls$ is non-zero or zero.
\end{theorem}
\begin{proof}
see \cite{tendler2015geometricclassfieldtheory} Propositions 3.13-3.14, or \cite{Toth2011} Prop 2.1.4:    

\end{proof}

%\subsection{Kummer Theory}
%\input{sections/Preliminaries/KummerTheory.tex}


\subsection{Behavior of Ramification under Product of Blowups}
Let $X$ and $Y$ be smooth schemes over a field $k$, and let $x \in X$ and $y \in Y$ be closed points. 
We denote the blowups of these schemes at the given points by 
$\pi_X: \Bl_x(X) \to X$ and $\pi_Y: \Bl_y(Y) \to Y$. Furthermore, let $\pi_{X \times Y}: \Bl_{(x,y)}(X \times_k Y) \to X \times_k Y$ 
be the blowup of the product scheme at the point $(x,y)$.
We denote by $E_X, E_Y$, and $E_{X \times Y}$ the respective exceptional divisors, and let $\eta_X, \eta_Y$, and $\eta_{X \times Y}$ be their generic points.

 In this section, we establish the following result concerning the stability of ramification bounds under the external product of torsors.

\begin{prop}\label{prop:ramification-external-product}
Let $G$ be a finite abelian group. Suppose $\cG_X$ and $\cG_Y$ are $G$-torsors defined on open subsets $U_X \subset \Bl_x(X)$ and $U_Y \subset \Bl_y(Y)$ that are disjoint 
from the exceptional divisors. 
If the ramification of $\cG_X$ at $\eta_X$ and $\cG_Y$ at $\eta_Y$ is bounded by $r$, then the external product torsors 
\[
\cG_{X \times Y} := \text{pr}_1^{-1} \cG_X \otimes \text{pr}_2^{-1} \cG_Y
\]
has ramification bounded by $r$ at the generic point $\eta_{X\times Y}$ of the exceptional divisor in the product blowup.
\end{prop}

The proposition is purely local in nature, it suffices to consider the case where $X$ and $Y$ are affine. 
More precisely, by the smoothness of $X$ and $Y$, we may restrict our attention to open neighborhoods of $x$ and $y$ that are isomorphic to affine spaces. 
The rest of this section treats that case.

\subsubsection*{The Affine Case}
Let $X = \mathbb{A}_k^n$ be the affine $n$-space over a field $k$, and let $0 \in X$ be the origin. 
Let $\tilde{X} = \text{Bl}_0(X)$ be the blowup of $X$ at the origin. 
Recall that $\tilde{X} \subset X \times_k \mathbb{P}^{n-1}_k$ is defined by the equations $x_i u_j = x_j u_i$, where $[u_1 : \dots : u_n]$ are the homogeneous coordinates of 
$\mathbb{P}^{n-1}_k$.
The exceptional divisor $E \subset \tilde{X}$ is the fiber over the origin, $E = \{ (0, [u_1 : \dots : u_n]) \}$, which is of codimension 1 in $\tilde{X}$. 
Let $\eta \in E$ be the generic point of $E$, and let $R = \mathcal{O}_{\tilde{X}, \eta}$ be the associated local ring. 
This ring $R$ is a discrete valuation ring (DVR) with fraction field $K = K(X) = k(x_1, \dots, x_n)$.

On the affine chart $U_1$ where $u_1 \neq 0$, we have $x_i = \frac{u_i}{u_1} x_1$. 
The coordinate ring is:$$\mathcal{O}_{\tilde{X}}(U_1) = k\left[x_1, \frac{u_2}{u_1}, \dots, \frac{u_n}{u_1}\right]$$
In this chart, the generic point $\eta$ corresponds to the prime ideal $\mathfrak{p}_1 = (x_1)$. Thus, the local ring is $R = k[x_1, \frac{u_2}{u_1}, \dots, \frac{u_n}{u_1}]_{(x_1)}$. 
The residue field is $\kappa(\eta) = k(\frac{u_2}{u_1}, \dots, \frac{u_n}{u_1})$, and the completion of $R$ with respect to its maximal ideal is:
$$\hat{R} = \kappa(\eta)[[x_1]]$$
In this local ring, $x_1$ is a uniformizer. Note that any $x_i$ (for $i > 1$) can also serve as a uniformizer, 
as $x_i = (\frac{u_i}{u_1}) x_1$ and $\frac{u_i}{u_1}$ is a unit in $R$.

For any monomial $M = x_1^{a_1} \dots x_n^{a_n} \in K$, we can write:
$$M = x_1^{\sum a_i} \left( \frac{u_2}{u_1} \right)^{a_2} \dots \left( \frac{u_n}{u_1} \right)^{a_n}$$
Since the term in parentheses is a unit in $R$, the valuation $\nu_E$ associated with $E$ satisfies:
$$\nu_E(M) = \sum a_i = \deg M$$
Consequently, for any polynomial $f = f_d + f_{d+1} + \dots + f_l$, where $f_i$ is the homogeneous part of degree $i$, we have $\nu_E(f) = d$ (the order of vanishing at the origin).

\subsubsection*{The Product Case}
Now, let $X = \mathbb{A}^n$ and $Y = \mathbb{A}^m$ with origins $x=0$ and $y=0$. 
As before, $\text{Bl}_0(X) \subset X \times \mathbb{P}^{n-1}$ and $\text{Bl}_0(Y) \subset Y \times \mathbb{P}^{m-1}$ have exceptional divisors $E_X$ and $E_Y$ respectively.
Consider the product $X \times_k Y \cong \mathbb{A}_k^{n+m}$. 
The blowup of the product at the origin $(0,0)$, denoted $\text{Bl}_{(0,0)}(X \times_k Y)$, is a subscheme of $(X \times Y) \times \mathbb{P}^{n+m-1}$ defined by:

$$\begin{cases} 
x_i w_j = x_j w_i & 1 \le i, j \le n \\
y_k w_{n+l} = y_l w_{n+k} & 1 \le k, l \le m \\
x_i w_{n+j} = y_j w_i & 1 \le i \le n, \,\, 1 \le j \le m 
\end{cases}$$
where $[w_1 : \dots : w_{n+m}]$ are the homogeneous coordinates of $\mathbb{P}^{n+m-1}$. The exceptional divisor $E_{X \times Y}$ is isomorphic to $\mathbb{P}^{n+m-1}$.

\subsubsection*{Comparison of Blowups}

Both $\text{Bl}_0(X) \times_k \text{Bl}_0(Y)$ and $\text{Bl}_{(0,0)}(X \times_k Y)$ are birational to $X \times_k Y$. 
They share a common dense open set $\tilde{U}$ defined by the condition that neither the $X$-coordinates nor the $Y$-coordinates vanish simultaneously in the projective space:
$$\tilde{U} = \{ ((x,y), [w_1: \dots : w_{n+m}]) \mid (w_1, \dots, w_n) \neq 0 \text{ and } (w_{n+1}, \dots, w_{n+m}) \neq 0 \}$$This yields a diagram of open immersions:
$$ 
   \begin{tikzcd}
        & \tilde{U} \arrow[dl, "f_1"'] \arrow[dr, "f_2", hook] & \\
        \text{Bl}_0(X) \times_k \text{Bl}_0(Y) & & \text{Bl}_{(0,0)}(X \times_k Y)
    \end{tikzcd}
$$
    
    where $f_1$ maps the coordinates to the respective projectivizations $[w_1: \dots : w_n]$ and $[w_{n+1}: \dots : w_{n+m}]$.
    Also note that the generic point $\eta_{X \times Y}$  of $E_{X \times_k Y}$ is inside $\tilde{U}$

\subsubsection*{Extensions of DVRs}
Let $S$ be the local ring of the generic point $\eta_{X\times Y}$ of $E_{X \times Y}$ in $\tilde{U}$. 
On the chart where $w_1 \neq 0$ and $w_{n+1} \neq 0$, we have 
$x_1 = (\frac{w_1}{w_{n+1}}) y_1$. 
Since $\frac{w_1}{w_{n+1}}$ is a unit in this chart, $x_1$ and $y_1$ are equivalent as uniformizers.
We have:
$$
S=k\left[x_1, \frac{w_2}{w_1} \cdots, \frac{w_n}{w_1}, \frac{w_{n+1}}{w_1} \cdots \frac{w_{n+m}}{w_1}\right]_{(x_1)} = 
k\left[\frac{w_1}{w_{n+1}}, \frac{w_2}{w_{n+1}} \cdots \frac{w_n}{w_{n+1}}, y_1 \cdots \frac{w_{n+m}}{w_{n+1}}\right]_{(y_1)}
$$

$$k(\eta_{X \times Y}) = k\left(\frac{w_2}{w_1} \cdots, \frac{w_n}{w_1}, \frac{w_{n+1}}{w_1} \cdots \frac{w_{n+m}}{w_1}\right)$$

Let $R_X$ be the local ring of the exceptional divisor $E_X$ in $\text{Bl}_0(X)$. 
The pullback of $E_X \times_k \text{Bl}_0(Y)$ along $f_1$ induces an extension of DVRs $R_X \hookrightarrow S$. Which is:
\begin{enumerate}
    \item Weakly Unramified: $x_1$ is a uniformizer in both $R_X$ and $S$, so the ramification index is $e=1$.
    \item Residually Transcendental: The residue field extension $\kappa(\eta_X) \subset \kappa(\eta)$ is:
    $$k\left(\frac{w_2}{w_1}, \dots, \frac{w_n}{w_1}\right) \subset k\left(\frac{w_2}{w_1}, \dots, \frac{w_n}{w_1}, \frac{w_{n+1}}{w_1}, \dots, \frac{w_{n+m}}{w_1}\right)$$
    Hence separable.
\end{enumerate}
Since this extension is generated by transcendental elements, it is separable and formally smooth at the maximal ideal (\stackstag{09E7}).

\subsubsection*{Ramification of $G$-Torsors}
Let $G$ be a finite abelian group. 
Let $\mathcal{Q}$ be a $G$-torsor on an open $U \subset \text{Bl}_0(X)$ disjoint from $E_X$. 
%Suppose $\mathcal{Q}$ has ramification bounded by $r$ at the generic point $\eta_X$ of $E_X$.
Let $V \subset \text{Bl}_0(Y)$ be an open subscheme, and let $\pi_X: \text{Bl}_0(X) \times_k V \to \text{Bl}_0(X)$ 
be the projection onto the first factor. 
By restricting this projection to $U \times_k V$, we obtain the pullback $G$-torsor:
$$\pi_X^{-1}(\mathcal{Q}) \cong \mathcal{Q} \times_k V$$
which is defined on the open subset $U \times_k V \subset \text{Bl}_0(X) \times_k \text{Bl}_0(Y)$.
The extension of local rings $R_X \to S$ is weakly unramified (the ramification index $e=1$) and residually transcendental with seprable residue field exntesion. 
Under these conditions the ramification filtration is preserved. 
Therefore, the pullback $\pi_X^{-1}(\mathcal{Q})$ has ramification bounded by $r$ at the generic point $\eta_{X \times Y}$ of the exceptional divisor $E_{X \times Y}$ if and only if 
the original torsor $\mathcal{Q}$ has ramification bounded by $r$ at the generic point $\eta_X$ of $E_X$

And we finish by \Cref{lemma:bounding_ramification_of_contracted_product}.



\subsection{Compactification of Blowup of Symmetric Powers of a Curve}\label{section:BlowupOfSymmetricPowerOfCurves}
We recall that our objective is to descend the local system $\cF^{(d)}$ from $U^{(d)}$ to $\PicCm[d]$ along the 
Abel-Jacobi map $\Phi_d$:

\[
\begin{tikzcd}
 \cF^{(d)} \arrow[d, purple]\\
 U^{(d)} \arrow[r, "\Phi_d"] & \PicCm[d]      
\end{tikzcd}
\]


(Here, the purple arrow emphasizes that the morphism is of sheaves on the étale site).

However, we encounter an obstruction: in the case we are considering ($\mdls > 0$), 
the fibers of $\Phi_d$ are affine spaces (of the same degree) rather than the better-behaved projective spaces. 
This hint that a solution to this problem is to compactify the morphism to yield projective fibers. 
 
This section describes the result of the compactification constructed by \cite{takeuchi2019blow} 
via the method of blowup.

Let $\mdls = \sum_{i=1}^n k_P P$ with $\deg P = d_P$ be a modulus on $C$, and let $d$ satisfy 
\Cref{equation:degree-condition}. 
Takeuchi (\cite{takeuchi2019blow}) defines $Z_0=Z_0(\mathfrak{m}, d)$ as the closed subscheme of 
$C^{(d)}$ defined by the map $C^{(d - \deg \mathfrak{m})} \to C^{(d)}$ adding $\mathfrak{m}$. 
He also defines $X_{\mathfrak{m}, d}$ as the blowup of $C^{(d)}$ along $Z_0$.
Let $E_0 = E_{\mathfrak{m},d} = Z_0(\mathfrak{m}, d) \times_{C^{(d)}} X_{\mathfrak{m}, d}$ be the exceptional divisor of the blowup. It is irreducible of codimension 1, and we let $\eta_0=\eta_{\mathfrak{m}, d}$ be its generic point.

%This section describes the compactification constructed by Takeuchi \cite{takeuchi2019blow} using the blowup method

% Let $\mdls = \sum_{i=1}^n k_P P$ with $\deg P = d_P$ be a modulus on $C$. Let $d$ satisfy \Cref{equation:degree-condition}.
% Takeuchi (\cite{takeuchi2019blow}) defines $Z_0=Z_0(\mdls, d)$ as the closed subscheme of $C^{(d)}$ defined by the map $C^{(d - \deg \mdls)} \to C^{(d)}$ adding $\mdls$.
% He also defines $X_{\mdls, d}$ as the blowup of $C^{(d)}$ along $Z_0$. 
% Let $E_0 = E_{\mdls,d} = Z_0(\mdls, d) \times_{C^{(d)}} X_{\mdls, d}$ 
% be the exceptional divisor of the blowup, it is irreducible of codimension 1, let $\eta_0=\eta_{\mdls, d}$ be its generic point.

Diagrammatically:
\[\begin{tikzcd}
\overline{\{\eta_0 \}} =  E_0 \arrow[r] \arrow[d] & X_{\mdls, d} \arrow[d, "\pi"] \\
Z_0 \arrow[r, "c.i"]           & C^{(d)}          
\end{tikzcd}\] 

Incoporating $U^{(d)}$, the local system $\cF^{(d)}$ and the Abel-Jacobi map, we have:
\[
\begin{tikzcd}
    & & \cF^{(d)} \arrow[d, purple]\\
\overline{\{\eta_0 \}} =  E_0 \arrow[r] \arrow[d] & 
X_{\mdls, d} \arrow[d, "\pi"]  & \arrow[l, hook'] \arrow[dl, hook'] U^{(d)} \arrow[r, "\Phi_d"] & \PicCm[d] \\
Z_0 \arrow[r, "c.i"]           & C^{(d)}          
\end{tikzcd}
\] 

In Section 3 of \cite{takeuchi2019blow} Takeuchi constructs, for large enough $d$ a compactification denoted by $\Cmod{d}$ and proves the following:
\textcolor{red}{exactly determined the fate of that d}

\begin{theorem}[Takeuchi]\label{theorem:takeuchi-compactification-theorem}
    The scheme $\Cmod{d}$ is an open subscheme of $X_{\mdls,d}$ containing $U^{(d)}$. 
    The morphism $\Phi_d: U^{(d)} \to \PicCm[d]$ extends to a morphism $\tilde{\Phi}_d: \Cmod{d} \to \PicCm[d]$ which makes 
    $\Cmod{d}$ a projective space bundle over $\PicCm[d]$. 
    Furthermore, the complement of $U^{(d)}$ in $\Cmod{d}$ is isomorphic to the fiber product 
    $E_0 \times_{C^{(d)}} \Cmod{d}$.
\end{theorem}

\begin{proof}
    \textcolor{red}{Add outline of construction and proofs}
\end{proof}

Diagrammatically we have:
\[
\begin{tikzcd}
    &  & \cF^{(d)} \arrow[d, purple]\\
    E_0 \times_{C^{(d)}} \Cmod{d} \arrow[d] \arrow[r]  & \Cmod{d} \arrow[d, hook] \arrow[rd, "\tilde{\Phi}_d"]  & U^{(d)} \arrow[l, hook'] \arrow[d, "\Phi_d"] \\
\overline{\{\eta_0 \}} =  E_0 \arrow[r] \arrow[d] & 
X_{\mdls, d} \arrow[d, "\pi"]  &  \PicCm[d] &  \\
Z_0 \arrow[r, "c.i"]           & C^{(d)}          
\end{tikzcd}
\] 

Also note that $ E_0 \times_{C^{(d)}} \Cmod{d} = Z_0 \times_{C^{(d)}} \Cmod{d}$


% \begin{equation}
% \begin{tikzcd}
%     % Row 1
%     & 
%     & U^{(d)} \arrow[d, hook, blue, dashed]  
%     \arrow[dd, hook, blue, dashed, bend right=25]
%      \arrow[ddd, hook, blue, dashed, bend right=40]
%       \arrow[dr, "\Phi_d"]
%     & 
%     \\
%     % Row 2
%     &  
%     &  \arrow[r, red] \arrow[d,  hook, red] \arrow[dr, phantom, "\square"]
%     & \PicCm[d] \arrow[d, hook, red] \\
%     % Row 3
%     & Z_0 \times_{C^{(d)}} X_{\mdls, d}  \arrow[r] \arrow[d]
%     & X_{\mdls, d} \arrow[r, red] \arrow[d, red]    
%     & P_{\mdls}^{d} \arrow[d, red] \\
%     % Row 4
%     & Z_0 \arrow[r]
%     & C^{(d)}
%     & \PicC[d]
% \end{tikzcd}
% \end{equation}

% %We remind, following the introduction, is that our mission is to decsend $\cF^{(d)}$ to $\PicCm[d]$ via $\Phi_d$. For this we don't consider the blowup. 

% In this section we define the blowup of $C^{(d)}$ by $Z_0$ and give its basic properties. As outlined in \cite{takeuchi2019blow}
% Let $C^{(d)}$ be the $d$'th symmetric product of $C$, which parametrizes effective Cartier
% divisor of $deg = d$ on $C$. Let $Z_0$ be the closed subscheme of $C^{(d)}$ defined by the map 
% And let $X_{\mdls, d}$ be the blowup of $C^{(d)}$ along $Z_0$.
% In \cite{takeuchi2019blow}[Section 3] Takeuchi proves:
% \begin{theorem}
%     There exists a commutative diagram:
%     \begin{equation}\label{diag:main-blowup-diag}
% \begin{tikzcd}
%     % Row 1
%     & 
%     & U^{(d)} \arrow[d, hook, blue, dashed]  \arrow[dd, hook, blue, dashed, bend right=25] \arrow[ddd, hook, blue, dashed, bend right=40] \arrow[dr, "\Phi_d"]
%     & 
%     \\
%     % Row 2
%     & Z_0 \times_{C^{(d)}} \Cmod{d}  \arrow[r] \arrow[d]
%     & \Cmod{d} \arrow[r, red] \arrow[d,  hook, red] \arrow[dr, phantom, "\square"]
%     & \PicCm[d] \arrow[d, hook, red] \\
%     % Row 3
%     & Z_0 \times_{C^{(d)}} X_{\mdls, d}  \arrow[r] \arrow[d]
%     & X_{\mdls, d} \arrow[r, red] \arrow[d, red]    
%     & P_{\mdls}^{d} \arrow[d, red] \\
%     % Row 4
%     & Z_0 \arrow[r]
%     & C^{(d)}
%     & \PicC[d]
% \end{tikzcd}
% \end{equation}
% Where
% \begin{enumerate}
%     \item \cite{takeuchi2019blow}[Lemma 3.1.] $P_\mdls^{d}$ is an etale sheaf on $Sch/S$ defined by:
%     $$P_{\mdls}^{d}(T) = \left\{ (\cL, \phi) \;\middle|\; \cL \in \operatorname{Pic}^{d}(C_T), \; \phi: \mathcal{O}_T \hookrightarrow pr_*(\cL/\cL(-\mdls)) \text{ s.t. } \operatorname{coker}(\phi) \text{ is loc. free} \right\} \Big/ \!\cong$$
%     (Isomorphism between two $(\cL, \phi), (\cL', \phi')$ is an isomorphism $f: \cL \xrightarrow{\cong} \cL'$ such that $pr_*(f) \circ \phi = \phi'$)
%     Moreover, it is represented by a proper smooth $S$-algebraic space. Assuming $C \to S$ has a section (\textcolor{red}{This seems rather imporant, it is also used to show $Pic_C^d$ as explicit expression as a sheaf, how do I refer to it }),
%     And letting $\cL'$ be a representative invertible sheaf of the universal class, \cite{takeuchi2019blow} shows that as sheaves on $Sch/\PicCm[d]$, $P_\mdls^d$ is isomorphic to the projectivization $\bP(pr_*(\cL'/\cL'(-\mdls)))$.
%     \item $\PicCm[d] \rightarrow P_\mdls^{d}$ is defined by $(\cL, \psi) \mapsto (\cL, \phi)$.  Where $\phi$ is defined as the composition
%     $$\Oo_T \to pr_* \Oo_{\mdls_T} \xrightarrow[]{pr_* \psi} pr_* (\cL/\cL(-\mdls)) $$. \cite{takeuchi2019blow}[Lemma 3.5] Shows this map is an open immersion.
%     \item The map $P_\mdls^d \to \PicCm[d]$ is by forgetting $\phi$
%     \item The definition of $X_{\mdls, d} \to P_\mdls$ is more technically involved, so we refer the reader to \cite{takeuchi2019blow}. But an imporant feature it is that
%     $X_{\mdls, d}$ is a projective space bundle over $P_\mdls^d$ via that map. 
%     \item $\Cmod{d}$ is an $S$-scheme, defined as the fibered product
%     \begin{tikzcd}
%     \Cmod{d} \arrow[r] \arrow[d, hook] 
%     & \mathrm{Pic}_{C,\mathfrak{m}}^{d} \arrow[d, hook] \\
%     X_{\mathfrak{m}} \arrow[r] 
%     & P_{\mathfrak{m}}^{d},
% \end{tikzcd}
% Hence, The $S$-Scheme $\Cmod{d}$ is a projective space bundle on $\PicCm[d]$ and an open subscheme of $X_{\mdls, d}$.
% \end{enumerate}
% Where for a scheme $X$ and a locally free sheaf of finite rank $\mathcal{F}$ on $X$. We use a contra-Grothendieck notation for a projective space. 
% Thus the $X$-scheme $\mathbb{P}(\mathcal{F})$ parametrizes invertible subsheaves of $\mathcal{F}$.

% Now focusing on the left side of \Cref{diag:main-blowup-diag}, \cite{takeuchi2019blow} shows:

% \begin{enumerate}[start=6]
%     \item $U^{(d)} \to \Cmod{d}$ is an open immersion, and as an open subscheme, $U^{(d)}$ is the complement of $Z_0 \times_{C^{(d)}} \Cmod{d}$
% \end{enumerate}
% \end{theorem}.

