
Next, we state the main theorem of geometric class field theory. And see how it relates to the classical class field theory.
This is copied from Daichi's and some adapated from Giroud's thesis:
Let $k$ be a perfect field, and let $C$ be a projective smooth geometrically connected curve over $k$. 
The geometric class field theory gives a geometric description of abelian coverings of $C$ by using generalized jacobian varieties. 
Let us recall its precise statement. 
Fix a modulus $\mdls$, i.e.\ an effective Cartier divisor of $C$ and let $U$ be its complement in $C$. 


The pairs $(\cL, \alpha)$, where $\cL$ is an invertible $\cO_C$-module and $\alpha$ is a rigidification of $\cL$ along $\mdls$, are parametrized by a $k$-group scheme $\PicCm$, called the rigidified Picard scheme.
The Abel-Jacobi morphism $$ \Phi : U \to \PicCm $$
is the morphism which sends a section $x$ of $U$ to the pair $(\cO(x), 1)$ . 
We prove the following version of geometric class field theory: 
\begin{theorem}[Geometric Class Field Theory]%\label{thm:GCFT}
    Let $\Lambda$ be a finite ring of cardinality invertible in $k$, and let $\cF$ be an \'etale sheaf of $\Lambda$-modules, locally free of rank 1 on $U$, with ramification bounded by $\mdls$. 
    Then, there exists a unique (up to isomorphism) \textit{multiplicative} \'etale sheaf of $\Lambda$-modules $\cG$ on $\PicCm$, locally free of rank 1, such that the pullback of $\cG$ by $\Phi$ is isomorphic to $\cF$.
\end{theorem}

Let $d$ be a positive integer. 
We denote by $U^{(d)}$ the $d$-th symmetric power of $U$ over $k$. 
For an \'etale sheaf $\cF$ on $U$, we denote by $\cF^{(d)}$ the $d$-th symmetric power of $\cF$ on $U^{(d)}$.
We have a natural morphism \textcolor{red}{Check if this morphism only work for large enough $d$?}
$$ \Phi_d : U^{(d)} \to \PicCm[d] $$
\textcolor{red}{is this actually the map?}
which sends a section $x_1 + \cdots + x_d$ of $U^{(d)}$ to the pair $(\cO(x_1 + \cdots + x_d), 1)$ .

Theorem \ref{thm:GCFT} can be reduced to the following statement:
\begin{theorem}\label{thm:GCFT_reduced_2}
    Let $\Lambda$ be a finite ring of cardinality invertible in $k$, and let $\cF$ be an \'etale sheaf of $\Lambda$-modules, locally free of rank 1 on $U$, with ramification bounded by $\mdls$. 
    Then, for sufficiently large integer $d$, there exists a unique (up to isomorphism) \textit{multiplicative} \'etale sheaf of $\Lambda$-modules $\cG_d$ on $\PicCm[d]$, locally free of rank 1, such that the pullback of $\cG_d$ by $\Phi_d$ is isomorphic to $\cF^{(d)}$.
\end{theorem}

\textcolor{red}{
 \begin{enumerate}
    \item A word about the decompositon of the Picard scheme into connected components indexed by degree.
    \item Definition of the abel jacobi-map, and its properties, its fibers, see how amichai does it. 
    \item Definition of multiplicative sheaves.
    \item Say something about the ramification condition.
    \item Put references inside the theorem like Giroud does
 \end{enumerate}
}

