\section{Preliminaries}
In this section we understand some prelimenaries.
Unless otherwise stated, we work within an arbitrary topos $\mathcal{E}$.

\subsection{Kummer Theory}
\input{sections/subsections/KummerTheory.tex}

\subsection{\texorpdfstring{The equivalence between $G$-torsors and locally free $\Lambda$-modules}{The equivalence between G-torsors and locally free Lambda-modules}}

The following proposition establishes the fundamental dictionary between the geometric theory
of principal homogeneous spaces and the algebraic theory of invertible modules.
This equivalence allows us to transport the monoidal structure from the category of modules
(the tensor product) to the category of torsors (the contracted product),
strictly within the categorical framework.


\begin{prop}
    Let $\mathcal{E}$ be a topos and let $\Lambda$ be a ring object in $\mathcal{E}$. Let $G = \Lambda^\times$ denote the internal group object of units of $\Lambda$.

    There is a canonical equivalence of monoidal categories between the category of $G$-torsors in $\mathcal{E}$ and the category of locally free $\Lambda$-modules of rank 1 in $\mathcal{E}$:
    \[
        \Phi: \mathbf{Tors}(\mathcal{E}, \Lambda^\times) \xrightarrow{\sim} \mathbf{Pic}(\mathcal{E}, \Lambda)
    \]
    The equivalence is defined by the associated module functor:
    \[
        P \longmapsto P \times^{\Lambda^\times} \Lambda := \Lambda^\times \backslash (\Lambda \times P)
    \]
    where the quotient is taken with respect to the diagonal action of $\Lambda^\times$ on $\Lambda \times P$. The inverse functor associates to an invertible module $L$ its sheaf of basis frames $\underline{\mathrm{Isom}}_\Lambda(\Lambda, L)$.
\end{prop}

In light of this canonical equivalence, we will pass freely between the language of $G$-torsors and that of locally free $\Lambda$-modules throughout the text.


\subsection{Ramification after Blowup}

For $P \to U$ a $G$-torsor. We denote by $P^{[d]} \to U^{(d)}$ the corresponding $G$-torsor over $U^{(d)}$.
Let $\eta^i$ be the generic point of the exceptional divisor $E^i$ of the blowup of $C^{(d_i n_i)}$ by $n_i P_i$
(Where $deg P_i = d_i$).
Where $P_i \in C \setminus U$
We want to prove:
\begin{prop}
    If $ram P^{[d_1n_1]}_{\eta^1} \leq k_1 $ and $ram P^{[d_2n_2]}_{\eta^2} \leq k_2 $
    Then $ram P^{[d_1n_1 + d_2n_2]}_{\eta} \leq max(k_1, k_2)$ where $\eta$ is the generic point of the exceptional divisor $E$ of the blowup of $C^{(d_1 n_1 + d_2n_2)}$ by $\mdls= n_1 P_1 + n_2P_2$
\end{prop}

We will work this out along an example:
Let $X=\bG_m=\spec R[t, t^{-1}]$ and Let $\cP=\bG_m \xrightarrow[]{(\cdot)^{n}} G_m$ be the $n$'th power map.
It is a $G=\Z/n\Z$ torsor.
The ring map is $R[t, t^{-1}] \xrightarrow[]{t \mapsto t^n} R[t, t^{-1}]$
which corresponds to ring extension: $R[t, t^{-1}] \to R[t^{\frac{1}{n}}, t^{-\frac{1}{n}}]$.
The field of fractions of $\bG_m$ is $K(t)$ and the corresponding map between fields of $\cP \to X$
is $K(t) \xrightarrow[]{t \to t^n} K(t)$. which corresponds to the field extension:
$K(t) \hookrightarrow K(t^{\frac{1}{n}}) = K(t)[X]/(X^n -t)$.
Where $K = Frac R$

The points $0, \infty \in \bP^1$ correspond to the local rings
$\Oo_{0} = K[t]_{(t)}$ and $\Oo_{\infty} = K[\frac{1}{t}]_{(\frac{1}{t})}$ of $K(t)$,
which are DVRs. The corresponding valuations of $K(t)$ are given by:
\[
    v_0\left(\frac{f}{g}\right) = \text{maximal exponent } n \text{ s.t. } t^{n} \mid \frac{f}{g}, \quad v_\infty\left(\frac{f}{g}\right) = \deg g - \deg f
\]

So the diagram of the G-torsor $\cP=\bG_m$ over $\bG_m$ is:
\begin{equation}
    \begin{tikzcd}
        & \cP=\mathbb{G}_m \ar[d, "(\cdot)^n"] \\
        \bP^1 & \arrow[l] \bG_m
    \end{tikzcd}
\end{equation}

The bounded ramification condition is given by:
\begin{equation}
    \text{ram } P_{\eta} \leq k
\end{equation}

We wish to understand


In the general case of a $G$ torsor $P \to C$ we have similarly:
$K(C) \cong K(t)$ the function ring of $C$ for some variable $t$ and a finite field extension $K/\F_p(t')$.
If the basefield $K$ contains $n$'th roots of unity, then the torsor is the same... and continue here:
$\Oo_{P_1}$
the same..
and continue.



This follows by the following:
Start talking about local rings, and take everything locally and prove it locally.
\begin{prop}
    Let
\end{prop}sss