
\subsection{Abel-Jacobi Map}
We copy from \cite{Toth2011}
We assume $d$ as in \Cref{equation:degree-condition}
\begin{definition}[Abel-Jacobi Map of degree d]
    
\end{definition}
The \textit{Abel-Jacobi map of degree d}
\[
\Phi_d: \text{Div}_C^d \to \text{Pic}_C^d
\]
is defined for a scheme $T$ over $\text{Spec}(k)$ and for a relative effective Cartier divisor $D$ of degree $d$ on $(C \times_{\text{Spec}(k)} T)/T$ by

\[
\Phi_d(T)(D) := [\mathcal{O}(D)]
\]
where $[\mathcal{O}(D)]$ is the class of the invertible sheaf $\mathcal{O}(D)$ on $(C \times_{\text{Spec}(k)} T)/T$. Equivalently if $D$ is represented by the pair $(\mathcal{G}, s)$ (1.2.6), then the Abel-Jacobi map is given by
\[
\Phi_d(T)((\mathcal{G}, s)) := [\mathcal{G}].
\]
A theorem in milne \cite{milneAV} shows that over a field $k$, for any $d\geq 1$ we have that 
the functor $\text{Div}_C^d$ is representable by the $d$-th symmetric power $C^{(d)}$. 

\subsubsection{Generalized Effective Cartier Divisors}
We copy from \cite{Guignard2018}
Let $f : X \to S$ be a smooth morphism of schemes of relative dimension 1, with connected
geometric fibers of genus $g$, which is Zariski-locally projective over $S$.

and let $i : Y \to X$ be a closed subscheme of $X$, which is finite locally free over $S$ of degree $N \ge 1$, 
and let $U = X \setminus Y$ be its complement. A \textbf{Y-trivial effective Cartier divisor of degree d on X} is a pair $(\mathcal{L}, \sigma)$ such that $\mathcal{L}$ is a locally free $\mathcal{O}_X$-module of rank 1 and $\sigma : \mathcal{O}_X \to \mathcal{L}$ is an injective homomorphism such that $i^*\sigma$ is an isomorphism and such that the closed subscheme $V(\sigma)$ of $X$ defined by the vanishing of the ideal $\sigma\mathcal{L}^{-1}$ of $\mathcal{O}_X$ is finite locally free of rank $d$ over $S$. Two $Y$-trivial effective divisors $(\mathcal{L}, \sigma)$ and $(\mathcal{L}', \sigma')$ are \textbf{equivalent} if there is an isomorphism $\beta : \mathcal{L} \to \mathcal{L}'$ of $\mathcal{O}_X$-modules such that $\beta\sigma = \sigma'$. 
As in \textcolor{red}{4.7 - This is not "trivial" show/or skip but say somethinig about it}, if such an isomorphism exists then it is unique.
\cite{Guignard2018} shows: 
\begin{prop}[4.11 In Guignard]
    The map $(\mathcal{L}, \sigma) \mapsto (V(\sigma) \hookrightarrow X)$ is a bijection from the set of equivalence classes of $Y$-trivial effective Cartiers divisor of degree $d$ on $X$ onto the set of closed subschemes of $U$ which are finite locally free of degree $d$ over $S$.
\end{prop}
\begin{prop}[4.12 In Guignard]
    Let $d$ be an integer and let $\text{Div}_{S}^{d, +}(X, Y)$ be the functor which to an $S$-scheme $T$ associates the set of equivalence classes of $Y_T$-trivial effective Cartier divisors of degree $d$ on $X_T$. Then $\text{Div}_{S}^{d, +}(X, Y)$ is representable by the $S$-scheme $\text{Sym}_S^d(U)$, the $d$-th symmetric power of $U = X \setminus Y$ over $S$. In particular $\text{Div}_{S}^{d, +}(X, Y)$ is smooth of relative dimension $d$ over $S$.
\end{prop}

\begin{prop}[4.14 In Guignard]
Let $d \geq N + 2g - 1$ be an integer, and let $\text{Pic}_{S}^d(X, Y)$ be the inverse image of $\text{Pic}_S^d(X)$ by the natural morphism $\text{Pic}_S(X, Y) \to \text{Pic}_S(X)$. Then the Abel-Jacobi morphism
$$ \Phi_d : \text{Div}_S^{d, +}(X, Y) \to \text{Pic}_{S}^d(X, Y) $$
$$ (\mathcal{L}, \sigma) \mapsto (\mathcal{L}, i^* \sigma) $$
is surjective smooth of relative dimension $d - N - g + 1$ and it has geometrically connected fibers.
\textcolor{red}{$N$ is the degree of $Y$ so $\deg \mdls$ - replace it}
\end{prop}

\textcolor{red}{
\begin{enumerate}
    \item The notation here from giroud of $f$ is as $pr$ in takeuchi, so we need to make it precise in coheret
    \item Some places they work over a family of curves, and some places over $k$. - make this uniform as well. 
    \item Here gioured use the term $Y$, we need to formulate it like $\mdls$ and $N$ by $N=\deg \mdls$
    \item Maybe add somewhere the definition of $Sym_U$ like 2.22 in Guingard. ?
\end{enumerate}
}
\subsection{The Blowup}
In this section we define the blowup of $C^{(d)}$ by $Z_0$ and give its basic properties. As outlined in \cite{takeuchi2019blow}
Let $C^{(d)}$ be the $d$'th symmetric product of $C$, which parametrizes effective Cartier
divisor of $deg = d$ on $C$. Let $Z_0$ be the closed subscheme of $C^{(d)}$ defined by the map $C^{(d- \deg \mdls)} \to C^{(d)}$ adding $\mdls$.
And let $X_{\mdls}$ be the blowup of $C^{(d)}$ along $Z_0$.
In \cite{takeuchi2019blow}[Section 3] Takeuchi proves:
\begin{theorem}
    There exists a commutative diagram:
    \begin{equation}\label{diag:main-blowup-diag}
\begin{tikzcd}
    % Row 1
    & 
    & U^{(d)} \arrow[d, hook, blue, dashed]  \arrow[dd, hook, blue, dashed, bend right=25] \arrow[ddd, hook, blue, dashed, bend right=40] \arrow[dr, "\Phi_d"]
    & 
    \\
    % Row 2
    & Z_0 \times_{C^{(d)}} \Cmod{d}  \arrow[r] \arrow[d]
    & \Cmod{d} \arrow[r, red] \arrow[d,  hook, red] \arrow[dr, phantom, "\square"]
    & \PicCm[d] \arrow[d, hook, red] \\
    % Row 3
    & Z_0 \times_{C^{(d)}} X_\mdls  \arrow[r] \arrow[d]
    & X_{\mdls} \arrow[r, red] \arrow[d, red]    
    & P_{\mdls}^{d} \arrow[d, red] \\
    % Row 4
    & Z_0 \arrow[r]
    & C^{(d)}
    & \PicC[d]
\end{tikzcd}
\end{equation}
Where
\begin{enumerate}
    \item \cite{takeuchi2019blow}[Lemma 3.1.] $P_\mdls^{d}$ is an etale sheaf on $Sch/S$ defined by:
    $$P_{\mdls}^{d}(T) = \left\{ (\cL, \phi) \;\middle|\; \cL \in \operatorname{Pic}^{d}(C_T), \; \phi: \mathcal{O}_T \hookrightarrow pr_*(\cL/\cL(-\mdls)) \text{ s.t. } \operatorname{coker}(\phi) \text{ is loc. free} \right\} \Big/ \!\cong$$
    (Isomorphism between two $(\cL, \phi), (\cL', \phi')$ is an isomorphism $f: \cL \xrightarrow{\cong} \cL'$ such that $pr_*(f) \circ \phi = \phi'$)
    Moreover, it is represented by a proper smooth $S$-algebraic space. Assuming $C \to S$ has a section (\textcolor{red}{This seems rather imporant, it is also used to show $Pic_C^d$ as explicit expression as a sheaf, how do I refer to it }),
    And letting $\cL'$ be a representative invertible sheaf of the universal class, \cite{takeuchi2019blow} shows that as sheaves on $Sch/\PicCm[d]$, $P_\mdls^d$ is isomorphic to the projectivization $\bP(pr_*(\cL'/\cL'(-\mdls)))$.
    \item $\PicCm[d] \rightarrow P_\mdls^{d}$ is defined by $(\cL, \psi) \mapsto (\cL, \phi)$.  Where $\phi$ is defined as the composition
    $$\Oo_T \to pr_* \Oo_{\mdls_T} \xrightarrow[]{pr_* \psi} pr_* (\cL/\cL(-\mdls)) $$. \cite{takeuchi2019blow}[Lemma 3.5] Shows this map is an open immersion.
    \item The map $P_\mdls^d \to \PicCm[d]$ is by forgetting $\phi$
    \item The definition of $X_\mdls \to P_\mdls$ is more technically involved, so we refer the reader to \cite{takeuchi2019blow}. But an imporant feature it is that
    $X_\mdls$ is a projective space bundle over $P_\mdls^d$ via that map. 
    \item $\Cmod{d}$ is an $S$-scheme (\textcolor{red}{Is it obvious that it is an S-scheme, when the base is algebraic space?}) defined as the fibered product
    \begin{tikzcd}
    \Cmod{d} \arrow[r] \arrow[d, hook] 
    & \mathrm{Pic}_{C,\mathfrak{m}}^{d} \arrow[d, hook] \\
    X_{\mathfrak{m}} \arrow[r] 
    & P_{\mathfrak{m}}^{d},
\end{tikzcd}
Hence, The $S$-Scheme $\Cmod{d}$ is a projective space bundle on $\PicCm[d]$ and an open subscheme of $X_\mdls$.
\end{enumerate}
Where for a scheme $X$ and a locally free sheaf of finite rank $\mathcal{F}$ on $X$. We use a contra-Grothendieck notation for a projective space. 
Thus the $X$-scheme $\mathbb{P}(\mathcal{F})$ parametrizes invertible subsheaves of $\mathcal{F}$.

Now focusing on the left side of \Cref{diag:main-blowup-diag}, \cite{takeuchi2019blow} shows:

\begin{enumerate}[start=6]
    \item $U^{(d)} \to \Cmod{d}$ is an open immersion, and as an open subscheme, $U^{(d)}$ is the complement of $Z_0 \times_{C^{(d)}} \Cmod{d}$
\end{enumerate}
\end{theorem}.




\subsection{Other Completions }
\textcolor{red}{add reference or proof} $\cF^{(d)}$ can be extended to a sheaf on this compactification with tame ramification along the boundary.
The compactification, denoted by $\tilde{C}^{(d)}_\mdls$ is fibered over $\PicCm[d]$ with fibers isomorphic to projective spaces. 
Hence, \textcolor{red}{show/add ref/add explanation} 

Here we will show 
The compactification has  

blow-up $X_\mdls$ of $C^{(d)}$ along a the closed subscheme $Z_0 \subset C^{(d)}$ defined by the map:


\textcolor{red}{
    \begin{enumerate}
        \item Here, C is defined over S, a family of curves, usually?
        \item Maybe add a section about Symmetric Powers of a curve? probably should.
    \end{enumerate}
}
