Let $\mdls$ be an effective Cartier divisor on $C$, and let $d$ be a positive integer satisfying $d \geq max \{2g-1 + \deg \mdls, \deg \mdls\}$ where $g$ is the genus of $C$. 
We denote by $C^{(d)}$ the $d$-th symmetric power of $C$ over $k$.
By \textcolor{red}{add reference}, the fibers of the map \textcolor{red}{for d large enough? under what conditions?}
$$ \Phi_d : U^{(d)} \to \PicCm[d] $$ over any point are isomorphic to
$$
\begin{cases}
\mathbb{A}_k^{d - \deg \mdls - g + 1} & \text{if } m > 0 \\
\mathbb{P}_k^{d - g} & \text{if } m = 0
\end{cases}
$$


%More accurately, for a $k$-point of $\PicCm[d]$ corresponding to a pair $(\cL, \alpha)$ where $\cL$ is an invertible $\cO_C$-module of degree $d$ and $\alpha$ is a rigidification of $\cL$ along $\mdls$, the fiber of $\Phi_d$ over this point is isomorphic to the projective space of global sections of $\cL$ which restrict to $\alpha$ along $\mdls$:
%$$ \mathbb{P}(\Gamma_\mdls(C, \cL)) = \mathbb{P}(\{ s \in \Gamma(C, \cL) \mid s|_\mdls = \alpha \}) $$

One can show this makes $\Phi_d$ into a fibration in affine spaces or projective spaces, depending on whether $\mdls$ is non-zero or zero. 

Using a fundamental theorem about etale fundamental groups:
\begin{theorem}[Homotopy Exact Sequence \stackstag{0C0J}]
Let $f : X \to S$ be a flat proper morphism of finite presentation whose geometric fibres are connected and reduced. Assume $S$ is connected and let $\overline{s}$ be a geometric point of $S$. Then there is an exact sequence

\[ \pi _1(X_{\overline{s}}) \to \pi _1(X) \to \pi _1(S) \to 1 \]
of fundamental groups.
\end{theorem}

We get, in the case when $\mdls = 0$ (Hence $\Phi_d$ is smooth and proper) that there is an isomorphism of fundamental groups:
$$ \pi_1^{et}(C^{(d)}) \cong \pi_1^{et}(\PicC[d]) $$
Implying \cref{thm:GCFT_reduced} \textcolor{red}{explain exactly how, becuase here it is fundamental groups and there it is etale sheafves of $\Lambda$-modules}. Also, we need it to be \textbf{multiplicative}!

In the case when $\mdls > 0$, $\Phi_d$ is not proper anymore, so we cannot apply the homotopy exact sequence directly.
In \cite{takeuchi2019blow} Takeuchi constructs a compactifiaction of $U^{(d)}$ by adding a boundary hyperplane, $H$, over which $\cF^{(d)}$ is tamely ramified.
This compactification is denoted by $\Cmod{d}$, it has $U^{(d)}$ as an open subscheme with complement $H$. 

\textbf{This is a theorem we are going to prove in a different way:}
\begin{theorem}\label{theorem:SymmetricPowerOfSheafIsTamelyRamified}
     Let $\Lambda$ be a finite ring of cardinality invertible in $k$, and let $\cF$ be an \'etale sheaf of $\Lambda$-modules, locally free of rank 1 on $U$, with ramification bounded by $\mdls$. 
    Then, for sufficiently large integer $d$, $\cF^{(d)}$ is tamely ramified on $H$.
\end{theorem}
\textcolor{red}{Note that the above terminology of tamely ramified on $H$ is defined exactly when H is the complement of $U^{(d)}$, so I want to say something about it, or make it clear, or somehow define it someplace else and refer to it }

More over, this compactification, denoted by $\tilde{C}^{(d)}_\mdls$ is fibered over $\PicCm[d]$ with fibers isomorphic to projective spaces. Thus we get
$$ \pi_1(\tilde{C}^{(d)}_\mdls) \cong \pi_1(\PicCm[d])$$

From here, one can go in two routes, 
\textbf{Route 1} - Showing $ \ker \{\pi^{ab}_1(U^{(d)}) \to \pi^{ab}_1(\PicCm[d]) \} $ is pro-$p$ group. 

\textbf{Route 2} - Showing $$\pi^{t, ab}_1(U^{(d)}) \to \pi^{t,ab}_1(\PicCm[d])$$ is isomorphism to its image.  \textcolor{red}{here one needs to be precise.}

In both cases, one would then get \cref{thm:GCFT_reduced}.

We start by defintions and basic proposition of everything we need. 
